---
title: "Network Benchmark Analysis"
params:
  result_id: "all"
  note: null
output:
  html_document:
    toc: true
    toc_depth: 2
    code_folding: hide
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE, warning = FALSE, message = FALSE, fig.width = 13, fig.height = 7)

rmd_dir <- dirname(normalizePath(knitr::current_input(dir = TRUE)))
repo_root <- normalizePath(file.path(rmd_dir, "..", ".."))

source(file.path(repo_root, "analysis", "network", "prelude.r"))
options(scipen = 999)

result_id <- params$result_id
results_dir <- file.path(repo_root, "analysis", "network", result_id)

required_csvs <- c(
  "network_scenarios.csv",
  "network_iperf3.csv",
  "network_iperf3_intervals.csv",
  "network_sockperf.csv"
)

if (!all(file.exists(file.path(results_dir, required_csvs)))) {
  source(file.path(repo_root, "analysis", "network", "build_csv.R"), local = TRUE)
  write_network_csvs(repo_root = repo_root, run_spec = result_id)
}

csv_sql_path <- function(name) {
  gsub("'", "''", normalizePath(file.path(results_dir, name), mustWork = TRUE), fixed = TRUE)
}

sql("select 1")
con <- duckdbcons[[":memory:"]]
DBI::dbExecute(con, "drop table if exists scenarios")
DBI::dbExecute(con, "drop table if exists iperf3")
DBI::dbExecute(con, "drop table if exists iperf3_intervals")
DBI::dbExecute(con, "drop table if exists sockperf")
DBI::dbExecute(con, sprintf("create table scenarios as select * from read_csv_auto('%s')", csv_sql_path("network_scenarios.csv")))
DBI::dbExecute(con, sprintf("create table iperf3 as select * from read_csv_auto('%s')", csv_sql_path("network_iperf3.csv")))
DBI::dbExecute(con, sprintf("create table iperf3_intervals as select * from read_csv_auto('%s')", csv_sql_path("network_iperf3_intervals.csv")))
DBI::dbExecute(con, sprintf("create table sockperf as select * from read_csv_auto('%s')", csv_sql_path("network_sockperf.csv")))

format_placement <- function(x) {
  factor(x, levels = placement_levels, labels = placement_labels[placement_levels])
}

no_data <- function(msg) {
  show_no_data_plot(msg)
}

box_jitter <- function(df, x, y, fill = NULL, title = NULL, subtitle = NULL, ylab = NULL) {
  if (nrow(df) == 0) return(no_data("No data for this comparison."))
  mapping <- if (is.null(fill)) {
    aes(x = .data[[x]], y = .data[[y]])
  } else {
    aes(x = .data[[x]], y = .data[[y]], fill = .data[[fill]])
  }
  ggplot(df, mapping) +
    geom_boxplot(outlier.shape = NA, alpha = 0.7) +
    geom_jitter(width = 0.12, alpha = 0.55, size = 1.6) +
    scale_y_continuous(labels = comma, limits = c(0, NA), expand = expansion(mult = c(0, 0.06))) +
    labs(title = title, subtitle = subtitle, x = NULL, y = ylab, fill = NULL) +
    base_plot_theme()
}

delta_table <- function(table_name, metric_expr, benchmark_select_expr, benchmark_group_cols, benchmark_output_cols,
                        lower_is_better = FALSE, where_clause = "1 = 1") {
  direction_expr <- if (lower_is_better) "-1" else "1"
  group_cols <- paste(c("placement_class", "client_machine_type", "server_machine_type", "protocol", benchmark_group_cols, "os_tuning"), collapse = ", ")
  join_cols <- c("placement_class", "client_machine_type", "server_machine_type", "protocol", benchmark_group_cols)
  join_condition <- paste(sprintf("s.%s is not distinct from t.%s", join_cols, join_cols), collapse = "\n        and ")
  paired_select_cols <- paste(paste0("s.", c("placement_class", "client_machine_type", "protocol", benchmark_output_cols)), collapse = ", ")
  output_cols <- paste(c("placement_class", "client_machine_type", "protocol", benchmark_output_cols), collapse = ", ")
  order_cols <- paste(c("placement_class", "client_machine_type", "protocol", benchmark_output_cols), collapse = ", ")
  sql(glue::glue("
    with base as (
      select placement_class, client_machine_type, server_machine_type, protocol,
             {benchmark_select_expr},
             os_tuning, {metric_expr} as metric
      from {table_name}
      where {where_clause}
    ),
    agg as (
      select {group_cols},
             median(metric) as median_metric, count(*) as n
      from base
      where metric is not null
      group by {group_cols}
    ),
    paired as (
      select {paired_select_cols},
             s.median_metric as standard_median,
             t.median_metric as tuned_median,
             s.n as standard_n,
             t.n as tuned_n,
             ((t.median_metric - s.median_metric) / nullif(s.median_metric, 0)) * 100 as raw_delta_pct
      from agg s
      join agg t
        on {join_condition}
      where s.os_tuning = 'standard' and t.os_tuning = 'tuned'
    )
    select {output_cols},
           round(standard_median, 3) as standard_median,
           round(tuned_median, 3) as tuned_median,
           standard_n, tuned_n,
           round(raw_delta_pct, 2) as delta_pct,
           round(raw_delta_pct * {direction_expr}, 2) as improvement_pct
    from paired
    order by {order_cols}
  "))
}
```

```{r data-availability, include=FALSE}
counts <- sql("
select
  (select count(*) from scenarios) as scenarios,
  (select count(*) from iperf3) as iperf3_repetitions,
  (select count(*) from sockperf) as sockperf_repetitions,
  (select count(*) from iperf3_intervals) as iperf3_intervals,
  (select count(distinct run_id) from scenarios) as runs
")
```

This report analyzes network benchmark results from `r result_id`.

```{r note, results='asis', echo=FALSE}
if (!is.null(params$note) && nzchar(params$note)) {
  cat(sprintf("> %s\n\n", params$note))
}
```

# Data Coverage

The main analysis uses one row per benchmark repetition. iperf3 interval rows are kept for diagnostics only and are not treated as independent benchmark repetitions.

```{r filter-policy, echo=FALSE}
filter_policy <- data.frame(
  section = c(
    "TCP throughput",
    "UDP throughput",
    "UDP packet-size impact",
    "Latency placement impact",
    "Latency instance impact",
    "Latency message-size impact"
  ),
  default_filter = c(
    "protocol = tcp; tcp_length_bytes = 131072; stream count and OS tuning are separated by facets where relevant",
    "protocol = udp; broad comparisons use udp_length_bytes = 1492; UDP target rate and stream count are fixed or shown explicitly",
    "protocol = udp; client_machine_type = g2a.120d; udp_target_bitrate_gbit_per_sec = 90; packet size is shown on the x-axis",
    "sockperf; comparable placement pairs only; os_tuning is split into standard/tuned subsections; message sizes are limited to 64 B and 8192 B",
    "sockperf; placement_class = different-host-single-az; msg_size_bytes = 64; protocol and OS tuning are separated by facets",
    "sockperf; client_machine_type = g2a.120d; os_tuning = standard; message size is shown on the x-axis"
  )
)
kable(filter_policy, caption = "Default filters used to keep network comparisons comparable")
```

```{r coverage-counts}
kable(counts, caption = "Parsed network benchmark data")
```

```{r scenario-matrix}
scenario_matrix <- sql("
select run_id, scenario_name, placement_class, client_machine_type,
       client_availability_zone, server_availability_zone, os_tuning,
       count(*) over (partition by run_id, scenario_name) as scenario_rows
from scenarios
order by run_id, scenario_name
")
kable(scenario_matrix, caption = "Scenario coverage")
```

```{r benchmark-coverage}
benchmark_coverage <- sql("
select 'iperf3' as tool, protocol, benchmark_name, count(*) as repetitions
from iperf3
group by 1, 2, 3
union all
select 'sockperf' as tool, protocol, benchmark_name, count(*) as repetitions
from sockperf
group by 1, 2, 3
order by tool, protocol, benchmark_name
")
kable(benchmark_coverage, caption = "Benchmark repetition coverage")
```

# Throughput

Throughput plots use `network_iperf3.csv`, one row per iperf3 repetition. The primary metric is receiver throughput in Mbit/s. Broad TCP comparisons fix `tcp_length_bytes = 131072` because this is the only TCP payload size currently present. Broad UDP comparisons fix `udp_length_bytes = 1492`; the dedicated packet-size section compares `1492` and `9000` bytes. UDP throughput must be interpreted together with loss and jitter.

## Placement Impact

Two placement comparisons are currently meaningful:

- `g2a.2d`: co-located single-AZ vs different-host single-AZ.
- `g2a.120d`: different-host single-AZ vs multi-AZ.

```{r tcp-placement-g2a2d, fig.width=13, fig.height=6.5}
tcp_place_2d <- sql("
select placement_class, os_tuning, parallel_streams,
       receiver_mbit_per_sec
from iperf3
where protocol = 'tcp'
  and tcp_length_bytes = 131072
  and client_machine_type = 'g2a.2d'
  and placement_class in ('co-located-single-az', 'different-host-single-az')
")
if (nrow(tcp_place_2d) == 0) {
  no_data("No comparable g2a.2d TCP placement data.")
} else {
  tcp_place_2d$placement_class <- format_placement(tcp_place_2d$placement_class)
  tcp_place_2d$stream_label <- paste0(tcp_place_2d$parallel_streams, " stream(s)")
  box_jitter(
    tcp_place_2d, "placement_class", "receiver_mbit_per_sec", "placement_class",
    "TCP throughput: co-located vs different-host (g2a.2d)",
    "Fixed tcp_length_bytes = 131072; facets keep stream count and OS tuning separate.",
    "Receiver throughput (Mbit/s)"
  ) +
    facet_grid(os_tuning ~ stream_label) +
    guides(fill = "none")
}
```

```{r tcp-placement-g2a120d, fig.width=13, fig.height=6.5}
tcp_place_120d <- sql("
select placement_class, os_tuning, parallel_streams,
       receiver_mbit_per_sec
from iperf3
where protocol = 'tcp'
  and tcp_length_bytes = 131072
  and client_machine_type = 'g2a.120d'
  and placement_class in ('different-host-single-az', 'multi-az')
")
if (nrow(tcp_place_120d) == 0) {
  no_data("No comparable g2a.120d TCP placement data.")
} else {
  tcp_place_120d$placement_class <- format_placement(tcp_place_120d$placement_class)
  tcp_place_120d$stream_label <- paste0(tcp_place_120d$parallel_streams, " stream(s)")
  box_jitter(
    tcp_place_120d, "placement_class", "receiver_mbit_per_sec", "placement_class",
    "TCP throughput: single-AZ vs multi-AZ (g2a.120d)",
    "Fixed tcp_length_bytes = 131072; facets keep stream count and OS tuning separate.",
    "Receiver throughput (Mbit/s)"
  ) +
    facet_grid(os_tuning ~ stream_label) +
    guides(fill = "none")
}
```

```{r udp-placement-summary}
udp_placement_summary <- sql("
select placement_class, client_machine_type, os_tuning,
       udp_target_bitrate_gbit_per_sec as target_gbps,
       udp_length_bytes, parallel_streams,
       count(*) as n,
       round(median(receiver_mbit_per_sec), 1) as median_recv_mbps,
       round(median(lost_percent), 2) as median_loss_pct,
       round(median(jitter_ms), 4) as median_jitter_ms
from iperf3
where protocol = 'udp'
  and udp_length_bytes = 1492
group by 1, 2, 3, 4, 5, 6
order by placement_class, client_machine_type, os_tuning, target_gbps, udp_length_bytes, parallel_streams
")
kable(udp_placement_summary, caption = "UDP throughput, loss, and jitter by placement and benchmark parameters; fixed udp_length_bytes = 1492")
```

## Instance Type Impact

Instance type comparisons fix placement to `different-host-single-az` to avoid mixing unrelated placement classes. Current data supports this comparison across `g2a.2d`, `g2a.8d`, and `g2a.120d`.

```{r tcp-instance-impact, fig.width=13, fig.height=6.5}
tcp_instance <- sql("
select placement_class, client_machine_type, os_tuning, parallel_streams,
       receiver_mbit_per_sec
from iperf3
where protocol = 'tcp'
  and tcp_length_bytes = 131072
  and placement_class = 'different-host-single-az'
")
if (nrow(tcp_instance) == 0) {
  no_data("No comparable TCP instance type data.")
} else {
  tcp_instance$placement_class <- format_placement(tcp_instance$placement_class)
  tcp_instance$stream_label <- paste0(tcp_instance$parallel_streams, " stream(s)")
  ggplot(tcp_instance, aes(x = client_machine_type, y = receiver_mbit_per_sec, fill = client_machine_type)) +
    geom_boxplot(outlier.shape = NA, alpha = 0.7) +
    geom_jitter(width = 0.12, alpha = 0.55, size = 1.6) +
    facet_grid(os_tuning ~ stream_label) +
    scale_y_continuous(labels = comma, limits = c(0, NA), expand = expansion(mult = c(0, 0.06))) +
    labs(
      title = "TCP throughput by instance type",
      subtitle = "Filtered to different-host single-AZ and tcp_length_bytes = 131072.",
      x = NULL, y = "Receiver throughput (Mbit/s)", fill = "Instance type"
    ) +
    base_plot_theme()
}
```

```{r udp-instance-impact, fig.width=13, fig.height=6.5}
udp_instance <- sql("
select placement_class, client_machine_type, os_tuning, parallel_streams,
       receiver_mbit_per_sec, lost_percent
from iperf3
where protocol = 'udp'
  and udp_length_bytes = 1492
  and placement_class = 'different-host-single-az'
  and udp_target_bitrate_gbit_per_sec = 90
")
if (nrow(udp_instance) == 0) {
  no_data("No comparable UDP instance type data.")
} else {
  udp_instance$placement_class <- format_placement(udp_instance$placement_class)
  udp_instance$stream_label <- paste0(udp_instance$parallel_streams, " stream(s)")
  ggplot(udp_instance, aes(x = client_machine_type, y = receiver_mbit_per_sec, fill = client_machine_type)) +
    geom_boxplot(outlier.shape = NA, alpha = 0.7) +
    geom_jitter(width = 0.12, alpha = 0.55, size = 1.6) +
    facet_grid(os_tuning ~ stream_label) +
    scale_y_continuous(labels = comma, limits = c(0, NA), expand = expansion(mult = c(0, 0.06))) +
    labs(
      title = "UDP throughput by instance type",
      subtitle = "Filtered to different-host single-AZ, udp_target_bitrate_gbit_per_sec = 90, and udp_length_bytes = 1492.",
      x = NULL, y = "Receiver throughput (Mbit/s)", fill = "Instance type"
    ) +
    base_plot_theme()
}
```

## OS Tuning Impact

The OS tuning table pairs standard and tuned measurements only when placement, instance type, protocol, and explicit benchmark parameters match.

```{r throughput-tuning-table}
throughput_tuning <- delta_table(
  "iperf3",
  "receiver_mbit_per_sec",
  "parallel_streams,
   tcp_length_bytes,
   udp_length_bytes,
   udp_target_bitrate_gbit_per_sec as udp_target_gbit_per_sec",
  c("parallel_streams", "tcp_length_bytes", "udp_length_bytes", "udp_target_gbit_per_sec"),
  c("parallel_streams", "tcp_length_bytes", "udp_length_bytes", "udp_target_gbit_per_sec"),
  lower_is_better = FALSE,
  where_clause = "receiver_mbit_per_sec is not null
                  and ((protocol = 'tcp' and tcp_length_bytes = 131072)
                       or (protocol = 'udp' and udp_length_bytes = 1492))"
)
kable(throughput_tuning, caption = "OS tuning impact on iperf3 receiver throughput; paired by explicit benchmark parameter columns")
```

## Protocol And UDP-Specific Effects

TCP and UDP have different benchmark semantics, so this section emphasizes protocol-specific behavior rather than treating them as equivalent.

```{r tcp-stream-impact, fig.width=12, fig.height=6}
tcp_stream <- sql("
select placement_class, client_machine_type, os_tuning, parallel_streams,
       receiver_mbit_per_sec
from iperf3
where protocol = 'tcp'
  and tcp_length_bytes = 131072
  and client_machine_type = 'g2a.120d'
")
if (nrow(tcp_stream) == 0) {
  no_data("No TCP data.")
} else {
  tcp_stream$placement_class <- format_placement(tcp_stream$placement_class)
  tcp_stream$stream_label <- paste0(tcp_stream$parallel_streams, " stream(s)")
  ggplot(tcp_stream, aes(x = stream_label, y = receiver_mbit_per_sec, fill = stream_label)) +
    geom_boxplot(outlier.shape = NA, alpha = 0.7) +
    geom_jitter(width = 0.12, alpha = 0.55, size = 1.5) +
    facet_grid(placement_class ~ os_tuning) +
    scale_y_continuous(labels = comma, limits = c(0, NA), expand = expansion(mult = c(0, 0.06))) +
    labs(
      title = "TCP stream count impact",
      subtitle = "Filtered to client_machine_type = 'g2a.120d' and tcp_length_bytes = 131072; placement and OS tuning are separated by facets.",
      x = NULL, y = "Receiver throughput (Mbit/s)", fill = NULL
    ) +
    base_plot_theme()
}
```

```{r udp-throughput-loss, fig.width=14, fig.height=7}
udp_loss <- sql("
select placement_class, client_machine_type, os_tuning,
       concat(cast(udp_target_bitrate_gbit_per_sec as varchar), ' Gbit/s, ',
              cast(parallel_streams as varchar), ' stream(s)') as udp_case,
       receiver_mbit_per_sec, lost_percent
from iperf3
where protocol = 'udp'
  and udp_length_bytes = 1492
  and client_machine_type = 'g2a.120d'
")
if (nrow(udp_loss) == 0) {
  no_data("No UDP data.")
} else {
  udp_loss$placement_class <- format_placement(udp_loss$placement_class)
  ggplot(udp_loss, aes(x = udp_case, y = lost_percent, fill = placement_class)) +
    geom_boxplot(outlier.shape = NA, alpha = 0.7) +
    geom_jitter(width = 0.12, alpha = 0.55, size = 1.5) +
    facet_grid(placement_class ~ os_tuning, scales = "free_x", space = "free_x") +
    scale_y_continuous(labels = label_percent(scale = 1), limits = c(0, NA), expand = expansion(mult = c(0, 0.06))) +
    labs(
      title = "UDP packet loss by target rate",
      subtitle = "Filtered to client_machine_type = 'g2a.120d' and udp_length_bytes = 1492; packet-size effects are shown separately.",
      x = NULL, y = "Lost packets (%)", fill = "Placement"
    ) +
    base_plot_theme() +
    theme(axis.text.x = element_text(angle = 35, hjust = 1), legend.position = "none")
}
```

```{r udp-jitter-table}
udp_jitter <- sql("
select placement_class, client_machine_type, os_tuning,
       udp_target_bitrate_gbit_per_sec as target_gbps,
       udp_length_bytes, parallel_streams,
       count(*) as n,
       round(median(jitter_ms), 4) as median_jitter_ms,
       round(max(jitter_ms), 4) as max_jitter_ms
from iperf3
where protocol = 'udp'
  and udp_length_bytes = 1492
  and client_machine_type = 'g2a.120d'
group by 1, 2, 3, 4, 5, 6
order by placement_class, client_machine_type, os_tuning, target_gbps, udp_length_bytes, parallel_streams
")
kable(udp_jitter, caption = "UDP jitter summary; filtered to client_machine_type = 'g2a.120d' and fixed udp_length_bytes = 1492")
```

## Packet And Message Size Impact

The broad throughput comparisons above keep packet/message size fixed. This section isolates the available size dimensions.

```{r tcp-size-summary}
tcp_size_summary <- sql("
select tcp_length_bytes, count(*) as n,
       round(median(receiver_mbit_per_sec), 1) as median_recv_mbps,
       round(min(receiver_mbit_per_sec), 1) as min_recv_mbps,
       round(max(receiver_mbit_per_sec), 1) as max_recv_mbps
from iperf3
where protocol = 'tcp'
group by 1
order by 1
")
kable(tcp_size_summary, caption = "TCP payload-size coverage. Current data has only one TCP length, so there is no TCP size comparison yet.")
```

```{r udp-packet-size-impact, fig.width=13, fig.height=8.5}
udp_size <- sql("
select placement_class, client_machine_type, os_tuning, parallel_streams,
       udp_length_bytes, receiver_mbit_per_sec, lost_percent
from iperf3
where protocol = 'udp'
  and udp_target_bitrate_gbit_per_sec = 90
  and client_machine_type = 'g2a.120d'
")
if (nrow(udp_size) == 0 || length(unique(udp_size$udp_length_bytes)) < 2) {
  no_data("No comparable UDP packet-size data with at least two packet sizes.")
} else {
  udp_size$placement_class <- format_placement(udp_size$placement_class)
  udp_size$size_label <- paste0(udp_size$udp_length_bytes, " B")
  udp_size$stream_label <- paste0(udp_size$parallel_streams, " stream(s)")
  ggplot(udp_size, aes(x = size_label, y = receiver_mbit_per_sec, fill = size_label)) +
    geom_boxplot(outlier.shape = NA, alpha = 0.7) +
    geom_jitter(width = 0.12, alpha = 0.55, size = 1.5) +
    facet_grid(placement_class + os_tuning ~ stream_label) +
    scale_y_continuous(labels = comma, limits = c(0, NA), expand = expansion(mult = c(0, 0.06))) +
    labs(
      title = "UDP throughput by packet size",
      subtitle = "Filtered to g2a.120d and 90 Gbit/s target rate; placement, tuning, and stream count are separated.",
      x = "UDP packet size", y = "Receiver throughput (Mbit/s)", fill = "Packet size"
    ) +
    base_plot_theme()
}
```

```{r udp-packet-size-loss, fig.width=13, fig.height=8.5}
if (nrow(udp_size) == 0 || length(unique(udp_size$udp_length_bytes)) < 2) {
  no_data("No comparable UDP packet-size data with at least two packet sizes.")
} else {
  ggplot(udp_size, aes(x = size_label, y = lost_percent, fill = size_label)) +
    geom_boxplot(outlier.shape = NA, alpha = 0.7) +
    geom_jitter(width = 0.12, alpha = 0.55, size = 1.5) +
    facet_grid(placement_class + os_tuning ~ stream_label) +
    scale_y_continuous(labels = label_percent(scale = 1), limits = c(0, NA), expand = expansion(mult = c(0, 0.06))) +
    labs(
      title = "UDP packet loss by packet size",
      subtitle = "Same filtered subset as the packet-size throughput plot.",
      x = "UDP packet size", y = "Lost packets (%)", fill = "Packet size"
    ) +
    base_plot_theme()
}
```

# Latency

Latency plots use `network_sockperf.csv`, one row per sockperf repetition. The report includes average latency and tail percentiles. Tail latency values are summary percentiles emitted by sockperf per repetition, not raw per-message samples.

## Placement Impact

As with throughput, placement comparisons use comparable subsets.

### Standard OS Tuning

```{r latency-placement-g2a2d-standard, fig.width=14, fig.height=8}
lat_place_2d_standard <- sql("
with base as (
  select placement_class, os_tuning, protocol, msg_size_bytes,
         avg_rtt_us, p50_rtt_us, p99_rtt_us, p999_rtt_us
  from sockperf
  where client_machine_type = 'g2a.2d'
    and placement_class in ('co-located-single-az', 'different-host-single-az')
    and msg_size_bytes in (64, 8192)
    and os_tuning = 'standard'
)
select placement_class, os_tuning, protocol, msg_size_bytes, 'avg' as metric, avg_rtt_us as latency_us from base
union all
select placement_class, os_tuning, protocol, msg_size_bytes, 'p50' as metric, p50_rtt_us as latency_us from base
union all
select placement_class, os_tuning, protocol, msg_size_bytes, 'p99' as metric, p99_rtt_us as latency_us from base
union all
select placement_class, os_tuning, protocol, msg_size_bytes, 'p99.9' as metric, p999_rtt_us as latency_us from base
")
if (nrow(lat_place_2d_standard) == 0) {
  no_data("No comparable g2a.2d latency placement data for standard OS tuning.")
} else {
  lat_place_2d_standard$placement_class <- format_placement(lat_place_2d_standard$placement_class)
  lat_place_2d_standard$metric <- factor(lat_place_2d_standard$metric, levels = c("avg", "p50", "p99", "p99.9"))
  lat_place_2d_standard$msg_label <- paste0(lat_place_2d_standard$protocol, " / ", lat_place_2d_standard$msg_size_bytes, " B")
  ggplot(lat_place_2d_standard, aes(x = placement_class, y = latency_us, fill = placement_class)) +
    geom_boxplot(outlier.shape = NA, alpha = 0.7) +
    geom_jitter(width = 0.12, alpha = 0.55, size = 1.3) +
    facet_grid(metric ~ msg_label, scales = "free_y") +
    scale_y_continuous(labels = comma, limits = c(0, NA), expand = expansion(mult = c(0, 0.08))) +
    labs(
      title = "Latency: co-located vs different-host (g2a.2d)",
      subtitle = "Filtered to os_tuning = 'standard'; message sizes limited to 64 B and 8192 B.",
      x = NULL, y = "RTT (us)", fill = NULL
    ) +
    base_plot_theme() +
    guides(fill = "none")
}
```

```{r latency-placement-g2a120d-standard, fig.width=14, fig.height=8}
lat_place_120d_standard <- sql("
with base as (
  select placement_class, os_tuning, protocol, msg_size_bytes,
         avg_rtt_us, p50_rtt_us, p99_rtt_us, p999_rtt_us
  from sockperf
  where client_machine_type = 'g2a.120d'
    and placement_class in ('different-host-single-az', 'multi-az')
    and msg_size_bytes in (64, 8192)
    and os_tuning = 'standard'
)
select placement_class, os_tuning, protocol, msg_size_bytes, 'avg' as metric, avg_rtt_us as latency_us from base
union all
select placement_class, os_tuning, protocol, msg_size_bytes, 'p50' as metric, p50_rtt_us as latency_us from base
union all
select placement_class, os_tuning, protocol, msg_size_bytes, 'p99' as metric, p99_rtt_us as latency_us from base
union all
select placement_class, os_tuning, protocol, msg_size_bytes, 'p99.9' as metric, p999_rtt_us as latency_us from base
")
if (nrow(lat_place_120d_standard) == 0) {
  no_data("No comparable g2a.120d latency placement data for standard OS tuning.")
} else {
  lat_place_120d_standard$placement_class <- format_placement(lat_place_120d_standard$placement_class)
  lat_place_120d_standard$metric <- factor(lat_place_120d_standard$metric, levels = c("avg", "p50", "p99", "p99.9"))
  lat_place_120d_standard$msg_label <- paste0(lat_place_120d_standard$protocol, " / ", lat_place_120d_standard$msg_size_bytes, " B")
  ggplot(lat_place_120d_standard, aes(x = placement_class, y = latency_us, fill = placement_class)) +
    geom_boxplot(outlier.shape = NA, alpha = 0.7) +
    geom_jitter(width = 0.12, alpha = 0.55, size = 1.3) +
    facet_grid(metric ~ msg_label, scales = "free_y") +
    scale_y_continuous(labels = comma, limits = c(0, NA), expand = expansion(mult = c(0, 0.08))) +
    labs(
      title = "Latency: single-AZ vs multi-AZ (g2a.120d)",
      subtitle = "Filtered to os_tuning = 'standard'; message sizes limited to 64 B and 8192 B.",
      x = NULL, y = "RTT (us)", fill = NULL
    ) +
    base_plot_theme() +
    guides(fill = "none")
}
```

### Tuned OS Tuning

```{r latency-placement-g2a2d-tuned, fig.width=14, fig.height=8}
lat_place_2d_tuned <- sql("
with base as (
  select placement_class, os_tuning, protocol, msg_size_bytes,
         avg_rtt_us, p50_rtt_us, p99_rtt_us, p999_rtt_us
  from sockperf
  where client_machine_type = 'g2a.2d'
    and placement_class in ('co-located-single-az', 'different-host-single-az')
    and msg_size_bytes in (64, 8192)
    and os_tuning = 'tuned'
)
select placement_class, os_tuning, protocol, msg_size_bytes, 'avg' as metric, avg_rtt_us as latency_us from base
union all
select placement_class, os_tuning, protocol, msg_size_bytes, 'p50' as metric, p50_rtt_us as latency_us from base
union all
select placement_class, os_tuning, protocol, msg_size_bytes, 'p99' as metric, p99_rtt_us as latency_us from base
union all
select placement_class, os_tuning, protocol, msg_size_bytes, 'p99.9' as metric, p999_rtt_us as latency_us from base
")
if (nrow(lat_place_2d_tuned) == 0) {
  no_data("No comparable g2a.2d latency placement data for tuned OS tuning.")
} else {
  lat_place_2d_tuned$placement_class <- format_placement(lat_place_2d_tuned$placement_class)
  lat_place_2d_tuned$metric <- factor(lat_place_2d_tuned$metric, levels = c("avg", "p50", "p99", "p99.9"))
  lat_place_2d_tuned$msg_label <- paste0(lat_place_2d_tuned$protocol, " / ", lat_place_2d_tuned$msg_size_bytes, " B")
  ggplot(lat_place_2d_tuned, aes(x = placement_class, y = latency_us, fill = placement_class)) +
    geom_boxplot(outlier.shape = NA, alpha = 0.7) +
    geom_jitter(width = 0.12, alpha = 0.55, size = 1.3) +
    facet_grid(metric ~ msg_label, scales = "free_y") +
    scale_y_continuous(labels = comma, limits = c(0, NA), expand = expansion(mult = c(0, 0.08))) +
    labs(
      title = "Latency: co-located vs different-host (g2a.2d)",
      subtitle = "Filtered to os_tuning = 'tuned'; message sizes limited to 64 B and 8192 B.",
      x = NULL, y = "RTT (us)", fill = NULL
    ) +
    base_plot_theme() +
    guides(fill = "none")
}
```

```{r latency-placement-g2a120d-tuned, fig.width=14, fig.height=8}
lat_place_120d_tuned <- sql("
with base as (
  select placement_class, os_tuning, protocol, msg_size_bytes,
         avg_rtt_us, p50_rtt_us, p99_rtt_us, p999_rtt_us
  from sockperf
  where client_machine_type = 'g2a.120d'
    and placement_class in ('different-host-single-az', 'multi-az')
    and msg_size_bytes in (64, 8192)
    and os_tuning = 'tuned'
)
select placement_class, os_tuning, protocol, msg_size_bytes, 'avg' as metric, avg_rtt_us as latency_us from base
union all
select placement_class, os_tuning, protocol, msg_size_bytes, 'p50' as metric, p50_rtt_us as latency_us from base
union all
select placement_class, os_tuning, protocol, msg_size_bytes, 'p99' as metric, p99_rtt_us as latency_us from base
union all
select placement_class, os_tuning, protocol, msg_size_bytes, 'p99.9' as metric, p999_rtt_us as latency_us from base
")
if (nrow(lat_place_120d_tuned) == 0) {
  no_data("No comparable g2a.120d latency placement data for tuned OS tuning.")
} else {
  lat_place_120d_tuned$placement_class <- format_placement(lat_place_120d_tuned$placement_class)
  lat_place_120d_tuned$metric <- factor(lat_place_120d_tuned$metric, levels = c("avg", "p50", "p99", "p99.9"))
  lat_place_120d_tuned$msg_label <- paste0(lat_place_120d_tuned$protocol, " / ", lat_place_120d_tuned$msg_size_bytes, " B")
  ggplot(lat_place_120d_tuned, aes(x = placement_class, y = latency_us, fill = placement_class)) +
    geom_boxplot(outlier.shape = NA, alpha = 0.7) +
    geom_jitter(width = 0.12, alpha = 0.55, size = 1.3) +
    facet_grid(metric ~ msg_label, scales = "free_y") +
    scale_y_continuous(labels = comma, limits = c(0, NA), expand = expansion(mult = c(0, 0.08))) +
    labs(
      title = "Latency: single-AZ vs multi-AZ (g2a.120d)",
      subtitle = "Filtered to os_tuning = 'tuned'; message sizes limited to 64 B and 8192 B.",
      x = NULL, y = "RTT (us)", fill = NULL
    ) +
    base_plot_theme() +
    guides(fill = "none")
}
```

## Instance Type Impact

```{r latency-instance-impact, fig.width=14, fig.height=8.5}
lat_instance <- sql("
select placement_class, client_machine_type, os_tuning, protocol, msg_size_bytes,
       avg_rtt_us, p50_rtt_us, p99_rtt_us
from sockperf
where placement_class = 'different-host-single-az'
  and msg_size_bytes = 64
")
if (nrow(lat_instance) == 0) {
  no_data("No comparable latency instance type data.")
} else {
  lat_instance$placement_class <- format_placement(lat_instance$placement_class)
  lat_instance_long <- sql("
    with base as (
      select placement_class, client_machine_type, os_tuning, protocol, msg_size_bytes,
             avg_rtt_us, p50_rtt_us, p99_rtt_us
      from sockperf
      where placement_class = 'different-host-single-az'
        and msg_size_bytes = 64
    )
    select placement_class, client_machine_type, os_tuning, protocol, msg_size_bytes, 'avg' as metric, avg_rtt_us as latency_us from base
    union all
    select placement_class, client_machine_type, os_tuning, protocol, msg_size_bytes, 'p50' as metric, p50_rtt_us as latency_us from base
    union all
    select placement_class, client_machine_type, os_tuning, protocol, msg_size_bytes, 'p99' as metric, p99_rtt_us as latency_us from base
  ")
  lat_instance_long$metric <- factor(lat_instance_long$metric, levels = c("avg", "p50", "p99"))
  ggplot(lat_instance_long, aes(x = client_machine_type, y = latency_us, fill = client_machine_type)) +
    geom_boxplot(outlier.shape = NA, alpha = 0.7) +
    geom_jitter(width = 0.12, alpha = 0.55, size = 1.5) +
    facet_grid(metric + protocol ~ os_tuning) +
    scale_y_continuous(labels = comma, limits = c(0, NA), expand = expansion(mult = c(0, 0.08))) +
    labs(
      title = "Latency by instance type",
      subtitle = "Filtered to different-host single-AZ and 64 B messages.",
      x = NULL, y = "RTT (us)", fill = "Instance type"
    ) +
    base_plot_theme()
}
```

## OS Tuning Impact

```{r latency-tuning-table}
latency_tuning <- delta_table(
  "sockperf",
  "p99_rtt_us",
  "msg_size_bytes",
  c("msg_size_bytes"),
  c("msg_size_bytes"),
  lower_is_better = TRUE,
  where_clause = "p99_rtt_us is not null"
)
kable(latency_tuning, caption = "OS tuning impact on sockperf p99 latency; paired by msg_size_bytes; positive improvement means tuned is lower")
```

## Protocol And Message Size Impact

```{r latency-message-size, fig.width=14, fig.height=7}
lat_msg <- sql("
select placement_class, os_tuning, protocol, msg_size_bytes,
       p50_rtt_us, p99_rtt_us, p999_rtt_us
from sockperf
where os_tuning = 'standard'
  and client_machine_type = 'g2a.120d'
")
if (nrow(lat_msg) == 0) {
  no_data("No sockperf data for os_tuning = 'standard' and client_machine_type = 'g2a.120d'.")
} else {
  lat_msg_long <- sql("
    with base as (
      select placement_class, os_tuning, protocol, msg_size_bytes,
             p50_rtt_us, p99_rtt_us, p999_rtt_us
      from sockperf
      where os_tuning = 'standard'
        and client_machine_type = 'g2a.120d'
    )
    select placement_class, os_tuning, protocol, msg_size_bytes, 'p50' as metric, p50_rtt_us as latency_us from base
    union all
    select placement_class, os_tuning, protocol, msg_size_bytes, 'p99' as metric, p99_rtt_us as latency_us from base
    union all
    select placement_class, os_tuning, protocol, msg_size_bytes, 'p99.9' as metric, p999_rtt_us as latency_us from base
  ")
  lat_msg_long$placement_class <- format_placement(lat_msg_long$placement_class)
  lat_msg_long$metric <- factor(lat_msg_long$metric, levels = c("p50", "p99", "p99.9"))
  ggplot(lat_msg_long, aes(x = factor(msg_size_bytes), y = latency_us, fill = protocol)) +
    geom_boxplot(outlier.shape = NA, alpha = 0.7, position = position_dodge(width = 0.75)) +
    facet_grid(metric ~ placement_class, scales = "free_y") +
    scale_y_continuous(labels = comma, limits = c(0, NA), expand = expansion(mult = c(0, 0.08))) +
    labs(
      title = "Latency by message size and protocol",
      subtitle = "Filtered to os_tuning = 'standard' and client_machine_type = 'g2a.120d'; placement is separated by facets.",
      x = "Message size (bytes)", y = "RTT (us)", fill = "Protocol"
    ) +
    base_plot_theme()
}
```

# Diagnostics

This section uses interval-level iperf3 data to inspect run stability. It should not be used as the primary statistical sample for throughput comparisons.

```{r interval-diagnostics, fig.width=14, fig.height=7}
interval_diag <- sql("
select run_id, scenario_name, placement_class, os_tuning, benchmark_name, repetition,
       interval_start_sec, mbit_per_sec
from iperf3_intervals
where omitted = false
  and protocol = 'tcp'
  and benchmark_name = 'iperf3-tcp-1s'
")
if (nrow(interval_diag) == 0) {
  no_data("No interval diagnostics data.")
} else {
  interval_diag$placement_class <- format_placement(interval_diag$placement_class)
  ggplot(interval_diag, aes(x = interval_start_sec, y = mbit_per_sec, group = interaction(run_id, scenario_name, repetition), color = placement_class)) +
    geom_line(alpha = 0.35, linewidth = 0.5) +
    facet_grid(placement_class ~ os_tuning) +
    scale_y_continuous(labels = comma, limits = c(0, NA), expand = expansion(mult = c(0, 0.06))) +
    labs(
      title = "TCP throughput interval diagnostics",
      subtitle = "Each line is one repetition of iperf3-tcp-1s; this is a stability view, not the main aggregate sample.",
      x = "Interval start (s)", y = "Throughput (Mbit/s)", color = "Placement"
    ) +
    base_plot_theme()
}
```

# Appendix: OS Tuning Profile

The `tuned` label in this report corresponds to the `network-throughput` profile applied by `/opt/cloud-measuring/bin/apply-os-tuning.sh` on both benchmark nodes. The `standard` profile leaves the OS network settings unchanged.

```{r tuning-appendix, echo=FALSE}
tuning_parameters <- data.frame(
  category = c(
    "Queue discipline and congestion control",
    "Queue discipline and congestion control",
    "Socket buffer limits",
    "Socket buffer limits",
    "Socket buffer limits",
    "Socket buffer limits",
    "UDP buffer minimums",
    "UDP buffer minimums",
    "Connection backlog and packet processing",
    "Connection backlog and packet processing",
    "Connection backlog and packet processing",
    "Connection backlog and packet processing",
    "TCP/IP behavior",
    "TCP/IP behavior",
    "TCP/IP behavior",
    "Interface-local tuning",
    "Interface-local tuning"
  ),
  setting = c(
    "net.core.default_qdisc",
    "net.ipv4.tcp_congestion_control",
    "net.core.rmem_max",
    "net.core.wmem_max",
    "net.ipv4.tcp_rmem",
    "net.ipv4.tcp_wmem",
    "net.ipv4.udp_rmem_min",
    "net.ipv4.udp_wmem_min",
    "net.core.somaxconn",
    "net.core.netdev_max_backlog",
    "net.core.netdev_budget",
    "net.core.optmem_max",
    "net.ipv4.ip_local_port_range",
    "net.ipv4.tcp_tw_reuse",
    "net.ipv4.tcp_frto",
    "ethtool -G <primary_iface>",
    "ip link set <primary_iface> txqueuelen"
  ),
  tuned_value = c(
    "fq",
    "bbr",
    "134217728",
    "134217728",
    "4096 87380 67108864",
    "4096 65536 67108864",
    "16384",
    "16384",
    "32768",
    "32768",
    "1000",
    "65535",
    "1024 65535",
    "1",
    "0",
    "rx 1024 tx 1024",
    "10000"
  ),
  stringsAsFactors = FALSE
)
kable(tuning_parameters, caption = "Network-throughput OS tuning profile")
```
