---
title: "Storage Benchmark Analysis"
params:
  result_id: "all"
  note: null
  config_file: null
output:
  html_document:
    toc: true
    toc_depth: 2
    code_folding: hide
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE, warning = FALSE, message = FALSE, fig.width = 12, fig.height = 7)

rmd_dir <- dirname(normalizePath(knitr::current_input(dir = TRUE)))
repo_root <- normalizePath(file.path(rmd_dir, "..", ".."))

source(file.path(repo_root, "analysis", "storage", "prelude.r"))
options(scipen = 999)

result_id <- params$result_id
results_dir <- file.path(repo_root, "analysis", "storage", result_id)

required_csvs <- c(
  "storage_scenarios.csv",
  "storage_benchmarks.csv",
  "storage_fio.csv",
  "storage_failures.csv"
)

if (!all(file.exists(file.path(results_dir, required_csvs)))) {
  stop(sprintf("Missing storage CSVs in %s. Run analysis/storage/build_csv.R first.", results_dir))
}

csv_sql_path <- function(name) {
  gsub("'", "''", normalizePath(file.path(results_dir, name), mustWork = TRUE), fixed = TRUE)
}

sql("select 1")
con <- duckdbcons[[":memory:"]]
DBI::dbExecute(con, "drop table if exists scenarios")
DBI::dbExecute(con, "drop table if exists benchmarks")
DBI::dbExecute(con, "drop table if exists fio")
DBI::dbExecute(con, "drop table if exists failures")
DBI::dbExecute(con, sprintf("create table scenarios as select * from read_csv_auto('%s')", csv_sql_path("storage_scenarios.csv")))
DBI::dbExecute(con, sprintf("create table benchmarks as select * from read_csv_auto('%s')", csv_sql_path("storage_benchmarks.csv")))
DBI::dbExecute(con, sprintf("create table fio as select * from read_csv_auto('%s')", csv_sql_path("storage_fio.csv")))
DBI::dbExecute(con, sprintf("create table failures as select * from read_csv_auto('%s')", csv_sql_path("storage_failures.csv")))

default_report_config <- list(
  reference_machine_type = "g2a.120d",
  instance_comparison_block_performance_class = "storage_premium_perf12",
  local_instance_comparison_block_performance_class = "storage_premium_perf6",
  reference_block_performance_class = "storage_premium_perf29",
  local_instance_rw_mode = "randread",
  default_io_engine = "io_uring",
  throughput_block_size = "128k",
  throughput_iodepth = 16,
  iops_latency_block_size = "4k",
  iops_latency_iodepth = 32,
  default_numjobs = 1,
  psync_iodepth = 1,
  psync_numjobs = 1,
  block_size_comparison = data.frame(
    block_size = c("4k", "128k"),
    iodepth = c(32, 16),
    stringsAsFactors = FALSE
  ),
  performance_class_machine_types = c("g2a.8d", "g2a.30d", "g2a.120d"),
  preferred_machine_order = c("g2a.8d", "g2a.30d", "g2a.120d"),
  preferred_workload_order = c("randread", "randwrite", "read", "write"),
  preferred_engine_order = c("psync", "io_uring"),
  preferred_target_order = c("local", "block")
)

configured_keys <- character(0)
report_config <- default_report_config
if (!is.null(params$config_file) && nzchar(params$config_file)) {
  config_override <- jsonlite::fromJSON(params$config_file, simplifyDataFrame = TRUE)
  unknown_keys <- setdiff(names(config_override), names(default_report_config))
  if (length(unknown_keys) > 0) {
    stop(sprintf("Unknown storage report config keys: %s", paste(unknown_keys, collapse = ", ")))
  }
  configured_keys <- names(config_override)
  report_config[names(config_override)] <- config_override
}

discover_single <- function(column, current) {
  if (column %in% configured_keys) return(current)
  values <- sql(sprintf(
    "select distinct %s as value from fio where valid_measurement and %s is not null order by 1",
    column, column
  ))$value
  if (length(values) == 1) values[[1]] else current
}

report_config$reference_machine_type <- discover_single(
  "benchmark_machine_type", report_config$reference_machine_type
)
report_config$instance_comparison_block_performance_class <- discover_single(
  "block_volume_performance_class", report_config$instance_comparison_block_performance_class
)
report_config$local_instance_comparison_block_performance_class <- discover_single(
  "block_volume_performance_class", report_config$local_instance_comparison_block_performance_class
)
report_config$reference_block_performance_class <- discover_single(
  "block_volume_performance_class", report_config$reference_block_performance_class
)
report_config$local_instance_rw_mode <- discover_single(
  "benchmark_rw_mode", report_config$local_instance_rw_mode
)
report_config$throughput_block_size <- discover_single("block_size", report_config$throughput_block_size)
report_config$iops_latency_block_size <- discover_single("block_size", report_config$iops_latency_block_size)

discover_iodepth <- function(config_key, block_size) {
  if (config_key %in% configured_keys) return(report_config[[config_key]])
  values <- sql(sprintf(
    paste(
      "select distinct iodepth from fio",
      "where valid_measurement",
      "  and io_engine = %s",
      "  and block_size = %s",
      "order by 1"
    ),
    as.character(DBI::dbQuoteString(con, report_config$default_io_engine)),
    as.character(DBI::dbQuoteString(con, block_size))
  ))$iodepth
  if (length(values) == 1) values[[1]] else report_config[[config_key]]
}

report_config$throughput_iodepth <- discover_iodepth(
  "throughput_iodepth", report_config$throughput_block_size
)
report_config$iops_latency_iodepth <- discover_iodepth(
  "iops_latency_iodepth", report_config$iops_latency_block_size
)

if (!("block_size_comparison" %in% configured_keys)) {
  available_block_sizes <- sql("
  select distinct block_size, block_size_bytes, iodepth, io_engine
  from fio
  where valid_measurement
  order by block_size_bytes, iodepth
  ")
  available_block_sizes <- available_block_sizes[
    available_block_sizes$io_engine == report_config$default_io_engine,
    c("block_size", "iodepth"),
    drop = FALSE
  ]
  if (nrow(available_block_sizes) > 0) report_config$block_size_comparison <- unique(available_block_sizes)
}
if (!("performance_class_machine_types" %in% configured_keys)) {
  available_machine_types <- sql("
  select distinct benchmark_machine_type
  from fio
  where valid_measurement and benchmark_machine_type is not null
  order by 1
  ")$benchmark_machine_type
  report_config$performance_class_machine_types <- unique(c(
    report_config$preferred_machine_order[
      report_config$preferred_machine_order %in% available_machine_types
    ],
    available_machine_types
  ))
}

scalar_config <- report_config[!vapply(report_config, is.list, logical(1))]
scalar_config <- scalar_config[!vapply(scalar_config, function(x) length(x) > 1, logical(1))]
DBI::dbWriteTable(con, "report_config", as.data.frame(scalar_config, stringsAsFactors = FALSE), overwrite = TRUE)
DBI::dbWriteTable(con, "report_block_size_comparison", report_config$block_size_comparison, overwrite = TRUE)

append_discovered <- function(preferred, discovered) unique(c(preferred, discovered))
machine_levels <- append_discovered(
  report_config$preferred_machine_order,
  sql("select distinct benchmark_machine_type from fio order by 1")$benchmark_machine_type
)
workload_levels <- append_discovered(
  report_config$preferred_workload_order,
  sql("select distinct benchmark_rw_mode from fio order by 1")$benchmark_rw_mode
)
engine_levels <- append_discovered(
  report_config$preferred_engine_order,
  sql("select distinct io_engine from fio order by 1")$io_engine
)
block_size_levels <- sql("select distinct block_size, block_size_bytes from fio order by block_size_bytes")$block_size
target_levels <- append_discovered(
  report_config$preferred_target_order,
  sql("select distinct storage_target from fio order by 1")$storage_target
)
performance_class_machine_label <- function(position) {
  machines <- report_config$performance_class_machine_types
  if (length(machines) < position) sprintf("machine slot %d (not configured)", position) else machines[[position]]
}
perf_class_order <- sql("
select distinct block_volume_performance_class
from scenarios
where block_volume_performance_class is not null
order by block_volume_performance_class
")$block_volume_performance_class
perf_class_order <- perf_class_order[order(as.integer(sub(".*perf([0-9]+).*", "\\1", perf_class_order)))]

wrap_subtitle <- function(text, width = 78) {
  if (is.null(text) || !nzchar(text)) return(NULL)
  paste(strwrap(text, width = width), collapse = "\n")
}

apply_factor_levels <- function(df) {
  if ("benchmark_machine_type" %in% names(df)) {
    df$benchmark_machine_type <- factor(df$benchmark_machine_type, levels = machine_levels)
  }
  if ("benchmark_rw_mode" %in% names(df)) {
    df$benchmark_rw_mode <- factor(df$benchmark_rw_mode, levels = workload_levels)
  }
  if ("io_engine" %in% names(df)) {
    df$io_engine <- factor(df$io_engine, levels = engine_levels)
  }
  if ("block_size" %in% names(df)) {
    df$block_size <- factor(df$block_size, levels = block_size_levels)
  }
  if ("storage_target" %in% names(df)) {
    df$storage_target <- factor(df$storage_target, levels = target_levels)
  }
  if ("block_volume_performance_class" %in% names(df)) {
    df$block_volume_performance_class <- factor(df$block_volume_performance_class, levels = perf_class_order)
  }
  if ("latency_metric" %in% names(df)) {
    df$latency_metric <- factor(df$latency_metric, levels = c("avg", "p50", "p99", "p99.9"))
  }
  if ("execution_config" %in% names(df)) {
    df$execution_config <- factor(df$execution_config, levels = unique(df$execution_config))
  }
  df
}

metric_box <- function(df, x, y, fill = NULL, facet = "benchmark_rw_mode", title = NULL,
                       subtitle = NULL, ylab = NULL, ncol = 2, y_zero = TRUE) {
  if (nrow(df) == 0) return(show_no_data_plot("No data for this comparison."))
  df <- apply_factor_levels(df)
  mapping <- if (is.null(fill)) {
    aes(x = .data[[x]], y = .data[[y]])
  } else {
    aes(x = .data[[x]], y = .data[[y]], fill = .data[[fill]])
  }
  p <- ggplot(df, mapping) +
    geom_boxplot(outlier.shape = NA, alpha = 0.72) +
    geom_jitter(width = 0.12, alpha = 0.55, size = 1.5) +
    labs(title = title, subtitle = wrap_subtitle(subtitle), x = NULL, y = ylab, fill = NULL) +
    base_plot_theme()

  if (y_zero) {
    p <- p + scale_y_continuous(labels = comma, limits = c(0, NA), expand = expansion(mult = c(0, 0.06)))
  } else {
    p <- p + scale_y_continuous(labels = comma, expand = expansion(mult = c(0.02, 0.06)))
  }

  if (!is.null(facet)) {
    p <- p + facet_wrap(stats::as.formula(paste("~", facet)), ncol = ncol, scales = "fixed")
  }

  p + guides(fill = "none")
}

metric_summary <- function(df, group_cols, metric_col) {
  if (nrow(df) == 0) return(df)
  aggregate(
    df[[metric_col]],
    df[group_cols],
    function(x) c(median = median(x, na.rm = TRUE), min = min(x, na.rm = TRUE), max = max(x, na.rm = TRUE), n = length(x))
  )
}

render_performance_class_plots <- function(metric_expression, ylab, title_suffix,
                                           block_size_setting, iodepth_setting,
                                           heading_level = 3) {
  for (machine_type in report_config$performance_class_machine_types) {
    cat(sprintf("%s %s\n\n", paste(rep("#", heading_level), collapse = ""), machine_type))
    machine_literal <- as.character(DBI::dbQuoteString(con, machine_type))
    df <- sql(glue::glue("
    select block_volume_performance_class, benchmark_rw_mode,
           {metric_expression} as metric_value
    from fio
    where valid_measurement
      and benchmark_machine_type = {machine_literal}
      and storage_target = 'block'
      and io_engine = (select default_io_engine from report_config)
      and block_size = (select {block_size_setting} from report_config)
      and iodepth = (select {iodepth_setting} from report_config)
      and numjobs = (select default_numjobs from report_config)
      and block_volume_performance_class is not null
    "))
    print(metric_box(
      df,
      x = "block_volume_performance_class",
      y = "metric_value",
      fill = "block_volume_performance_class",
      title = sprintf("%s block storage %s by performance class", machine_type, title_suffix),
      ylab = ylab
    ))
    cat("\n\n")
  }
}

validate_rows <- sql("
select
  count(*) as fio_rows,
  sum(case when valid_measurement then 1 else 0 end) as valid_rows,
  sum(case when not valid_measurement then 1 else 0 end) as invalid_rows,
  count(distinct run_id) as runs
from fio
")

block_size_comparison_text <- paste(
  sprintf(
    "%s uses iodepth = %s",
    report_config$block_size_comparison$block_size,
    report_config$block_size_comparison$iodepth
  ),
  collapse = "; "
)

resolved_config <- data.frame(
  setting = c(
    "reference_machine_type",
    "instance_comparison_block_performance_class",
    "local_instance_comparison_block_performance_class",
    "reference_block_performance_class",
    "local_instance_rw_mode",
    "default_io_engine",
    "throughput_block_size",
    "throughput_iodepth",
    "iops_latency_block_size",
    "iops_latency_iodepth",
    "default_numjobs",
    "psync_iodepth",
    "psync_numjobs",
    "block_size_comparison"
  ),
  value = c(
    report_config$reference_machine_type,
    report_config$instance_comparison_block_performance_class,
    report_config$local_instance_comparison_block_performance_class,
    report_config$reference_block_performance_class,
    report_config$local_instance_rw_mode,
    report_config$default_io_engine,
    report_config$throughput_block_size,
    report_config$throughput_iodepth,
    report_config$iops_latency_block_size,
    report_config$iops_latency_iodepth,
    report_config$default_numjobs,
    report_config$psync_iodepth,
    report_config$psync_numjobs,
    block_size_comparison_text
  ),
  stringsAsFactors = FALSE
)
```

This report analyzes storage benchmark results from `r result_id`.

```{r note, results='asis', echo=FALSE}
if (!is.null(params$note) && nzchar(params$note)) {
  cat(sprintf("> %s\n\n", params$note))
}
```

# Overview

The report intentionally avoids using `benchmark_name` as a plot facet for impact analysis. The benchmark name is a derived label that includes dimensions such as block size and I/O engine. The plots below compare one dimension at a time while fixing the other relevant dimensions in SQL.

The renderer resolves its comparison constants before executing the plot queries. A passed JSON file overrides defaults. If a zoom-in dimension has exactly one available value, that value is selected automatically. The resolved values are shown below. Fixed comparisons filter `io_engine`, `block_size`, `iodepth`, and `numjobs` explicitly. Execution-configuration plots show the available combinations of `io_engine`, `iodepth`, and `numjobs`. Block-size comparisons apply the configured block-size-to-`iodepth` mapping.

```{r coverage-counts}
coverage_counts <- sql("
select
  (select count(*) from scenarios) as scenarios,
  (select count(*) from benchmarks) as benchmark_rows,
  (select count(*) from fio) as fio_rows,
  (select count(*) from failures) as failures,
  (select sum(case when valid_measurement then 1 else 0 end) from fio) as valid_fio_rows
")
kable(coverage_counts, caption = "Parsed storage benchmark data")
```

```{r filter-policy, echo=FALSE}
filter_policy <- data.frame(
  section = c("Throughput", "Throughput block-size impact", "IOPS", "Latency"),
  default_filter = c(
    sprintf(
      "block_size = %s, io_engine = %s, iodepth = %s, numjobs = %s",
      report_config$throughput_block_size, report_config$default_io_engine,
      report_config$throughput_iodepth, report_config$default_numjobs
    ),
    sprintf("io_engine = %s, numjobs = %s; %s", report_config$default_io_engine, report_config$default_numjobs, block_size_comparison_text),
    sprintf(
      "block_size = %s; %s uses iodepth = %s and numjobs = %s; psync uses iodepth = %s and numjobs = %s",
      report_config$iops_latency_block_size, report_config$default_io_engine,
      report_config$iops_latency_iodepth, report_config$default_numjobs,
      report_config$psync_iodepth, report_config$psync_numjobs
    ),
    sprintf(
      "block_size = %s, io_engine = %s, iodepth = %s, numjobs = %s",
      report_config$iops_latency_block_size, report_config$default_io_engine,
      report_config$iops_latency_iodepth, report_config$default_numjobs
    )
  )
)
kable(filter_policy, caption = "Default filtering policy")
```

```{r resolved-config, echo=FALSE}
kable(resolved_config, caption = "Resolved report configuration")
```

```{r scenario-table}
scenario_table <- sql("
select run_id, scenario_name, benchmark_machine_type, benchmark_availability_zone,
       os_tuning, access_mode, storage_targets_raw, block_volume_performance_class
from scenarios
order by run_id, scenario_name
")
kable(scenario_table, caption = "Scenario coverage")
```

```{r dimension-coverage}
dimension_coverage <- sql("
select benchmark_machine_type, block_volume_performance_class, storage_target,
       benchmark_rw_mode, io_engine, block_size, iodepth, numjobs,
       iodepth * numjobs as effective_concurrency,
       sum(case when valid_measurement then 1 else 0 end) as valid_repetitions
from fio
group by 1, 2, 3, 4, 5, 6, 7, 8, 9
order by 1, 2, 3, 4, 5, 6, 7, 8, 9
")
kable(dimension_coverage, caption = "Coverage by explicit analysis dimensions")
```

# Throughput

Throughput is reported as MiB/s using `primary_bw_bytes_per_sec`. Main comparisons use the resolved throughput subset shown in the configuration table.

## Instance Type Impact

### Block Storage

Filter values: see the resolved report configuration table above. Expand the collapsed code block to inspect the exact SQL predicate for this plot.

```{r throughput-instance, fig.width=12, fig.height=7}
throughput_instance <- sql("
select benchmark_machine_type, benchmark_rw_mode,
       primary_bw_bytes_per_sec / 1024.0 / 1024.0 as bw_mib_per_sec
from fio
where valid_measurement
  and storage_target = 'block'
  and block_volume_performance_class = (select instance_comparison_block_performance_class from report_config)
  and io_engine = (select default_io_engine from report_config)
  and block_size = (select throughput_block_size from report_config)
  and iodepth = (select throughput_iodepth from report_config)
  and numjobs = (select default_numjobs from report_config)
")
metric_box(
  throughput_instance,
  x = "benchmark_machine_type",
  y = "bw_mib_per_sec",
  fill = "benchmark_machine_type",
  title = "Block storage throughput by instance type",
  ylab = "Throughput (MiB/s)"
)
```

### Local Storage

Filter values: see the resolved report configuration table above. Expand the collapsed code block to inspect the exact SQL predicate for this plot.

```{r throughput-instance-local, fig.width=12, fig.height=5}
throughput_instance_local <- sql("
select benchmark_machine_type, benchmark_rw_mode,
       primary_bw_bytes_per_sec / 1024.0 / 1024.0 as bw_mib_per_sec
from fio
where valid_measurement
  and storage_target = 'local'
  and block_volume_performance_class = (select local_instance_comparison_block_performance_class from report_config)
  and benchmark_rw_mode = (select local_instance_rw_mode from report_config)
  and io_engine = (select default_io_engine from report_config)
  and block_size = (select iops_latency_block_size from report_config)
  and iodepth = (select iops_latency_iodepth from report_config)
  and numjobs = (select default_numjobs from report_config)
")
metric_box(
  throughput_instance_local,
  x = "benchmark_machine_type",
  y = "bw_mib_per_sec",
  fill = "benchmark_machine_type",
  title = "Local storage throughput by instance type",
  ylab = "Throughput (MiB/s)",
  ncol = 1
)
```

## Block Storage Performance Class Impact

Filter values: see the resolved report configuration table above. Expand the collapsed code block to inspect the exact SQL predicate for this plot.

```{r throughput-perf-class, results='asis', fig.width=12, fig.height=7}
render_performance_class_plots(
  "primary_bw_bytes_per_sec / 1024.0 / 1024.0",
  "Throughput (MiB/s)",
  "throughput",
  "throughput_block_size",
  "throughput_iodepth"
)
```

## Storage Target Impact

Filter values: see the resolved report configuration table above. Expand the collapsed code block to inspect the exact SQL predicate for this plot.

```{r throughput-target, fig.width=12, fig.height=7}
throughput_target <- sql("
select storage_target, benchmark_rw_mode,
       primary_bw_bytes_per_sec / 1024.0 / 1024.0 as bw_mib_per_sec
from fio
where valid_measurement
  and benchmark_machine_type = (select reference_machine_type from report_config)
  and block_volume_performance_class = (select reference_block_performance_class from report_config)
  and storage_target in ('local', 'block')
  and io_engine = (select default_io_engine from report_config)
  and block_size = (select throughput_block_size from report_config)
  and iodepth = (select throughput_iodepth from report_config)
  and numjobs = (select default_numjobs from report_config)
")
metric_box(
  throughput_target,
  x = "storage_target",
  y = "bw_mib_per_sec",
  fill = "storage_target",
  title = "Throughput by storage target",
  ylab = "Throughput (MiB/s)"
)
```

## Execution Configuration Impact

The execution configuration combines `io_engine`, `iodepth`, and `numjobs`. This makes concurrency differences explicit instead of attributing them to the I/O engine alone.

Filter values: see the resolved report configuration table above. Expand the collapsed code block to inspect the exact SQL predicate for this plot.

```{r throughput-execution-config, fig.width=12, fig.height=7}
throughput_execution_config <- sql("
select concat(io_engine, ' / q', cast(iodepth as varchar), ' / jobs=', cast(numjobs as varchar)) as execution_config,
       benchmark_rw_mode,
       primary_bw_bytes_per_sec / 1024.0 / 1024.0 as bw_mib_per_sec
from fio
where valid_measurement
  and benchmark_machine_type = (select reference_machine_type from report_config)
  and block_volume_performance_class = (select reference_block_performance_class from report_config)
  and storage_target = 'block'
  and block_size = (select throughput_block_size from report_config)
order by case when io_engine = 'io_uring' then 1 else 2 end, iodepth, numjobs
")
metric_box(
  throughput_execution_config,
  x = "execution_config",
  y = "bw_mib_per_sec",
  fill = "execution_config",
  title = "Throughput by execution configuration",
  ylab = "Throughput (MiB/s)"
)
```

### io_uring Queue Depth

This diagnostic fixes `io_engine` and `numjobs`, then compares `iodepth`.

```{r throughput-iouring-iodepth, fig.width=12, fig.height=7}
throughput_iouring_iodepth <- sql("
select concat('q', cast(iodepth as varchar)) as iodepth_config, benchmark_rw_mode,
       primary_bw_bytes_per_sec / 1024.0 / 1024.0 as bw_mib_per_sec
from fio
where valid_measurement
  and benchmark_machine_type = (select reference_machine_type from report_config)
  and block_volume_performance_class = (select reference_block_performance_class from report_config)
  and storage_target = 'block'
  and block_size = (select throughput_block_size from report_config)
  and io_engine = (select default_io_engine from report_config)
  and numjobs = (select default_numjobs from report_config)
")
metric_box(
  throughput_iouring_iodepth,
  x = "iodepth_config",
  y = "bw_mib_per_sec",
  fill = "iodepth_config",
  title = "io_uring throughput by queue depth",
  ylab = "Throughput (MiB/s)"
)
```

### psync Worker Count

This diagnostic fixes `io_engine = psync` and `iodepth`, then compares `numjobs`.

```{r throughput-psync-numjobs, fig.width=12, fig.height=7}
throughput_psync_numjobs <- sql("
select concat('jobs=', cast(numjobs as varchar)) as numjobs_config, benchmark_rw_mode,
       primary_bw_bytes_per_sec / 1024.0 / 1024.0 as bw_mib_per_sec
from fio
where valid_measurement
  and benchmark_machine_type = (select reference_machine_type from report_config)
  and block_volume_performance_class = (select reference_block_performance_class from report_config)
  and storage_target = 'block'
  and block_size = (select throughput_block_size from report_config)
  and io_engine = 'psync'
  and iodepth = (select psync_iodepth from report_config)
")
metric_box(
  throughput_psync_numjobs,
  x = "numjobs_config",
  y = "bw_mib_per_sec",
  fill = "numjobs_config",
  title = "psync throughput by worker count",
  ylab = "Throughput (MiB/s)"
)
```

## Block Size Impact

### Block Storage

Filter values: see the resolved report configuration table above. Expand the collapsed code block to inspect the exact SQL predicate for this plot.

```{r throughput-block-size, fig.width=12, fig.height=7}
throughput_block_size <- sql("
select block_size, benchmark_rw_mode,
       primary_bw_bytes_per_sec / 1024.0 / 1024.0 as bw_mib_per_sec
from fio
where valid_measurement
  and benchmark_machine_type = (select reference_machine_type from report_config)
  and block_volume_performance_class = (select reference_block_performance_class from report_config)
  and storage_target = 'block'
  and io_engine = (select default_io_engine from report_config)
  and numjobs = (select default_numjobs from report_config)
  and exists (
    select 1 from report_block_size_comparison comparison
    where comparison.block_size = fio.block_size
      and comparison.iodepth = fio.iodepth
  )
")
metric_box(
  throughput_block_size,
  x = "block_size",
  y = "bw_mib_per_sec",
  fill = "block_size",
  title = "Throughput by block size",
  ylab = "Throughput (MiB/s)"
)
```

### Local Storage

Filter values: see the resolved report configuration table above. Expand the collapsed code block to inspect the exact SQL predicate for this plot.

```{r throughput-block-size-local, fig.width=12, fig.height=7}
throughput_block_size_local <- sql("
select block_size, benchmark_rw_mode,
       primary_bw_bytes_per_sec / 1024.0 / 1024.0 as bw_mib_per_sec
from fio
where valid_measurement
  and benchmark_machine_type = (select reference_machine_type from report_config)
  and block_volume_performance_class = (select reference_block_performance_class from report_config)
  and storage_target = 'local'
  and io_engine = (select default_io_engine from report_config)
  and numjobs = (select default_numjobs from report_config)
  and exists (
    select 1 from report_block_size_comparison comparison
    where comparison.block_size = fio.block_size
      and comparison.iodepth = fio.iodepth
  )
")
metric_box(
  throughput_block_size_local,
  x = "block_size",
  y = "bw_mib_per_sec",
  fill = "block_size",
  title = "Local storage throughput by block size",
  ylab = "Throughput (MiB/s)"
)
```

```{r throughput-summary}
throughput_summary <- sql("
select benchmark_machine_type, block_volume_performance_class, storage_target,
       benchmark_rw_mode, io_engine, block_size, iodepth, numjobs,
       iodepth * numjobs as effective_concurrency,
       round(median(primary_bw_bytes_per_sec) / 1024.0 / 1024.0, 2) as median_mib_per_sec,
       round(avg(primary_bw_bytes_per_sec) / 1024.0 / 1024.0, 2) as avg_mib_per_sec,
       count(*) as repetitions
from fio
where valid_measurement
  and block_size = (select throughput_block_size from report_config)
  and io_engine = (select default_io_engine from report_config)
  and iodepth = (select throughput_iodepth from report_config)
  and numjobs = (select default_numjobs from report_config)
group by 1, 2, 3, 4, 5, 6, 7, 8, 9
order by 1, 2, 3, 4, 5, 6, 7, 8, 9
")
kable(throughput_summary, caption = sprintf("Throughput summary for %s %s measurements", report_config$default_io_engine, report_config$throughput_block_size))
```

# IOPS

IOPS is reported using `primary_iops`. Main comparisons use the resolved IOPS subset shown in the configuration table. Execution-configuration plots show the available engine, queue-depth, and worker-count combinations.

## Instance Type Impact

### Block Storage

Filter values: see the resolved report configuration table above. Expand the collapsed code block to inspect the exact SQL predicate for this plot.

```{r iops-instance, fig.width=12, fig.height=7}
iops_instance <- sql("
select benchmark_machine_type, benchmark_rw_mode, primary_iops as iops
from fio
where valid_measurement
  and storage_target = 'block'
  and block_volume_performance_class = (select instance_comparison_block_performance_class from report_config)
  and io_engine = (select default_io_engine from report_config)
  and block_size = (select iops_latency_block_size from report_config)
  and iodepth = (select iops_latency_iodepth from report_config)
  and numjobs = (select default_numjobs from report_config)
")
metric_box(
  iops_instance,
  x = "benchmark_machine_type",
  y = "iops",
  fill = "benchmark_machine_type",
  title = "Block storage IOPS by instance type",
  ylab = "IOPS"
)
```

### Local Storage

Filter values: see the resolved report configuration table above. Expand the collapsed code block to inspect the exact SQL predicate for this plot.

```{r iops-instance-local, fig.width=12, fig.height=5}
iops_instance_local <- sql("
select benchmark_machine_type, benchmark_rw_mode, primary_iops as iops
from fio
where valid_measurement
  and storage_target = 'local'
  and block_volume_performance_class = (select local_instance_comparison_block_performance_class from report_config)
  and benchmark_rw_mode = (select local_instance_rw_mode from report_config)
  and io_engine = (select default_io_engine from report_config)
  and block_size = (select iops_latency_block_size from report_config)
  and iodepth = (select iops_latency_iodepth from report_config)
  and numjobs = (select default_numjobs from report_config)
")
metric_box(
  iops_instance_local,
  x = "benchmark_machine_type",
  y = "iops",
  fill = "benchmark_machine_type",
  title = "Local storage IOPS by instance type",
  ylab = "IOPS",
  ncol = 1
)
```

## Block Storage Performance Class Impact

Filter values: see the resolved report configuration table above. Expand the collapsed code block to inspect the exact SQL predicate for this plot.

```{r iops-perf-class, results='asis', fig.width=12, fig.height=7}
render_performance_class_plots(
  "primary_iops",
  "IOPS",
  "IOPS",
  "iops_latency_block_size",
  "iops_latency_iodepth"
)
```

## Execution Configuration Impact

The execution configuration combines `io_engine`, `iodepth`, and `numjobs`. This makes concurrency differences explicit instead of attributing them to the I/O engine alone.

Filter values: see the resolved report configuration table above. Expand the collapsed code block to inspect the exact SQL predicate for this plot.

```{r iops-execution-config, fig.width=12, fig.height=7}
iops_execution_config <- sql("
select concat(io_engine, ' / q', cast(iodepth as varchar), ' / jobs=', cast(numjobs as varchar)) as execution_config,
       benchmark_rw_mode, primary_iops as iops
from fio
where valid_measurement
  and benchmark_machine_type = (select reference_machine_type from report_config)
  and block_volume_performance_class = (select reference_block_performance_class from report_config)
  and storage_target = 'block'
  and block_size = (select iops_latency_block_size from report_config)
order by case when io_engine = 'io_uring' then 1 else 2 end, iodepth, numjobs
")
metric_box(
  iops_execution_config,
  x = "execution_config",
  y = "iops",
  fill = "execution_config",
  title = "IOPS by execution configuration",
  ylab = "IOPS"
)
```

### io_uring Queue Depth

This diagnostic fixes `io_engine` and `numjobs`, then compares `iodepth`.

```{r iops-iouring-iodepth, fig.width=12, fig.height=7}
iops_iouring_iodepth <- sql("
select concat('q', cast(iodepth as varchar)) as iodepth_config, benchmark_rw_mode, primary_iops as iops
from fio
where valid_measurement
  and benchmark_machine_type = (select reference_machine_type from report_config)
  and block_volume_performance_class = (select reference_block_performance_class from report_config)
  and storage_target = 'block'
  and block_size = (select iops_latency_block_size from report_config)
  and io_engine = (select default_io_engine from report_config)
  and numjobs = (select default_numjobs from report_config)
")
metric_box(
  iops_iouring_iodepth,
  x = "iodepth_config",
  y = "iops",
  fill = "iodepth_config",
  title = "io_uring IOPS by queue depth",
  ylab = "IOPS"
)
```

### psync Worker Count

This diagnostic fixes `io_engine = psync` and `iodepth`, then compares `numjobs`.

```{r iops-psync-numjobs, fig.width=12, fig.height=7}
iops_psync_numjobs <- sql("
select concat('jobs=', cast(numjobs as varchar)) as numjobs_config, benchmark_rw_mode, primary_iops as iops
from fio
where valid_measurement
  and benchmark_machine_type = (select reference_machine_type from report_config)
  and block_volume_performance_class = (select reference_block_performance_class from report_config)
  and storage_target = 'block'
  and block_size = (select iops_latency_block_size from report_config)
  and io_engine = 'psync'
  and iodepth = (select psync_iodepth from report_config)
")
metric_box(
  iops_psync_numjobs,
  x = "numjobs_config",
  y = "iops",
  fill = "numjobs_config",
  title = "psync IOPS by worker count",
  ylab = "IOPS"
)
```

## Block Size Impact

### Block Storage

Filter values: see the resolved report configuration table above. Expand the collapsed code block to inspect the exact SQL predicate for this plot.

```{r iops-block-size, fig.width=12, fig.height=7}
iops_block_size <- sql("
select block_size, benchmark_rw_mode, primary_iops as iops
from fio
where valid_measurement
  and benchmark_machine_type = (select reference_machine_type from report_config)
  and block_volume_performance_class = (select reference_block_performance_class from report_config)
  and storage_target = 'block'
  and io_engine = (select default_io_engine from report_config)
  and numjobs = (select default_numjobs from report_config)
  and exists (
    select 1 from report_block_size_comparison comparison
    where comparison.block_size = fio.block_size
      and comparison.iodepth = fio.iodepth
  )
")
metric_box(
  iops_block_size,
  x = "block_size",
  y = "iops",
  fill = "block_size",
  title = "Block storage IOPS by block size",
  ylab = "IOPS"
)
```

### Local Storage

Filter values: see the resolved report configuration table above. Expand the collapsed code block to inspect the exact SQL predicate for this plot.

```{r iops-block-size-local, fig.width=12, fig.height=7}
iops_block_size_local <- sql("
select block_size, benchmark_rw_mode, primary_iops as iops
from fio
where valid_measurement
  and benchmark_machine_type = (select reference_machine_type from report_config)
  and block_volume_performance_class = (select reference_block_performance_class from report_config)
  and storage_target = 'local'
  and io_engine = (select default_io_engine from report_config)
  and numjobs = (select default_numjobs from report_config)
  and exists (
    select 1 from report_block_size_comparison comparison
    where comparison.block_size = fio.block_size
      and comparison.iodepth = fio.iodepth
  )
")
metric_box(
  iops_block_size_local,
  x = "block_size",
  y = "iops",
  fill = "block_size",
  title = "Local storage IOPS by block size",
  ylab = "IOPS"
)
```

## Storage Target Impact

Filter values: see the resolved report configuration table above. Expand the collapsed code block to inspect the exact SQL predicate for this plot.

```{r iops-target, fig.width=12, fig.height=7}
iops_target <- sql("
select storage_target, benchmark_rw_mode, primary_iops as iops
from fio
where valid_measurement
  and benchmark_machine_type = (select reference_machine_type from report_config)
  and block_volume_performance_class = (select reference_block_performance_class from report_config)
  and storage_target in ('local', 'block')
  and io_engine = (select default_io_engine from report_config)
  and block_size = (select iops_latency_block_size from report_config)
  and iodepth = (select iops_latency_iodepth from report_config)
  and numjobs = (select default_numjobs from report_config)
")
metric_box(
  iops_target,
  x = "storage_target",
  y = "iops",
  fill = "storage_target",
  title = "IOPS by storage target",
  ylab = "IOPS"
)
```

```{r iops-summary}
iops_summary <- sql("
select benchmark_machine_type, block_volume_performance_class, storage_target,
       benchmark_rw_mode, io_engine, block_size, iodepth, numjobs,
       iodepth * numjobs as effective_concurrency,
       round(median(primary_iops), 2) as median_iops,
       round(avg(primary_iops), 2) as avg_iops,
       count(*) as repetitions
from fio
where valid_measurement
  and block_size = (select iops_latency_block_size from report_config)
group by 1, 2, 3, 4, 5, 6, 7, 8, 9
order by 1, 2, 3, 4, 5, 6, 7, 8, 9
")
kable(iops_summary, caption = sprintf("IOPS summary for %s measurements", report_config$iops_latency_block_size))
```

# Latency

Latency is reported in microseconds. Main comparisons use the resolved latency subset shown in the configuration table. Execution-configuration plots show the available engine, queue-depth, and worker-count combinations.

## Latency Metric Overview

Filter values: see the resolved report configuration table above. Expand the collapsed code block to inspect the exact SQL predicate for this plot.

```{r latency-metric-overview, fig.width=12, fig.height=7}
latency_metric_overview <- sql("
select benchmark_rw_mode, 'avg' as latency_metric, primary_clat_mean_ns / 1000.0 as latency_us
from fio
where valid_measurement
  and benchmark_machine_type = (select reference_machine_type from report_config)
  and block_volume_performance_class = (select reference_block_performance_class from report_config)
  and storage_target = 'block'
  and io_engine = (select default_io_engine from report_config)
  and block_size = (select iops_latency_block_size from report_config)
  and iodepth = (select iops_latency_iodepth from report_config)
  and numjobs = (select default_numjobs from report_config)
union all
select benchmark_rw_mode, 'p50' as latency_metric, primary_clat_p50_ns / 1000.0 as latency_us
from fio
where valid_measurement
  and benchmark_machine_type = (select reference_machine_type from report_config)
  and block_volume_performance_class = (select reference_block_performance_class from report_config)
  and storage_target = 'block'
  and io_engine = (select default_io_engine from report_config)
  and block_size = (select iops_latency_block_size from report_config)
  and iodepth = (select iops_latency_iodepth from report_config)
  and numjobs = (select default_numjobs from report_config)
union all
select benchmark_rw_mode, 'p99' as latency_metric, primary_clat_p99_ns / 1000.0 as latency_us
from fio
where valid_measurement
  and benchmark_machine_type = (select reference_machine_type from report_config)
  and block_volume_performance_class = (select reference_block_performance_class from report_config)
  and storage_target = 'block'
  and io_engine = (select default_io_engine from report_config)
  and block_size = (select iops_latency_block_size from report_config)
  and iodepth = (select iops_latency_iodepth from report_config)
  and numjobs = (select default_numjobs from report_config)
union all
select benchmark_rw_mode, 'p99.9' as latency_metric, primary_clat_p999_ns / 1000.0 as latency_us
from fio
where valid_measurement
  and benchmark_machine_type = (select reference_machine_type from report_config)
  and block_volume_performance_class = (select reference_block_performance_class from report_config)
  and storage_target = 'block'
  and io_engine = (select default_io_engine from report_config)
  and block_size = (select iops_latency_block_size from report_config)
  and iodepth = (select iops_latency_iodepth from report_config)
  and numjobs = (select default_numjobs from report_config)
")
metric_box(
  latency_metric_overview,
  x = "latency_metric",
  y = "latency_us",
  fill = "latency_metric",
  title = "Latency distribution by metric",
  ylab = "Latency (us)"
)
```

## Instance Type Impact

### Block Storage

Filter values: see the resolved report configuration table above. Expand the collapsed code block to inspect the exact SQL predicate for this plot.

#### P99

```{r latency-instance, fig.width=12, fig.height=7}
latency_instance <- sql("
select benchmark_machine_type, benchmark_rw_mode,
       primary_clat_p99_ns / 1000.0 as latency_us
from fio
where valid_measurement
  and storage_target = 'block'
  and block_volume_performance_class = (select instance_comparison_block_performance_class from report_config)
  and io_engine = (select default_io_engine from report_config)
  and block_size = (select iops_latency_block_size from report_config)
  and iodepth = (select iops_latency_iodepth from report_config)
  and numjobs = (select default_numjobs from report_config)
")
metric_box(
  latency_instance,
  x = "benchmark_machine_type",
  y = "latency_us",
  fill = "benchmark_machine_type",
  title = "Block storage P99 latency by instance type",
  ylab = "P99 latency (us)"
)
```

#### P50

```{r latency-instance-p50, fig.width=12, fig.height=7}
latency_instance_p50 <- sql("
select benchmark_machine_type, benchmark_rw_mode,
       primary_clat_p50_ns / 1000.0 as latency_us
from fio
where valid_measurement
  and storage_target = 'block'
  and block_volume_performance_class = (select instance_comparison_block_performance_class from report_config)
  and io_engine = (select default_io_engine from report_config)
  and block_size = (select iops_latency_block_size from report_config)
  and iodepth = (select iops_latency_iodepth from report_config)
  and numjobs = (select default_numjobs from report_config)
")
metric_box(
  latency_instance_p50,
  x = "benchmark_machine_type",
  y = "latency_us",
  fill = "benchmark_machine_type",
  title = "Block storage P50 latency by instance type",
  ylab = "P50 latency (us)"
)
```

### Local Storage

Filter values: see the resolved report configuration table above. Expand the collapsed code block to inspect the exact SQL predicate for this plot.

#### P99

```{r latency-instance-local, fig.width=12, fig.height=5}
latency_instance_local <- sql("
select benchmark_machine_type, benchmark_rw_mode,
       primary_clat_p99_ns / 1000.0 as latency_us
from fio
where valid_measurement
  and storage_target = 'local'
  and block_volume_performance_class = (select local_instance_comparison_block_performance_class from report_config)
  and benchmark_rw_mode = (select local_instance_rw_mode from report_config)
  and io_engine = (select default_io_engine from report_config)
  and block_size = (select iops_latency_block_size from report_config)
  and iodepth = (select iops_latency_iodepth from report_config)
  and numjobs = (select default_numjobs from report_config)
")
metric_box(
  latency_instance_local,
  x = "benchmark_machine_type",
  y = "latency_us",
  fill = "benchmark_machine_type",
  title = "Local storage P99 latency by instance type",
  ylab = "P99 latency (us)",
  ncol = 1
)
```

#### P50

```{r latency-instance-local-p50, fig.width=12, fig.height=5}
latency_instance_local_p50 <- sql("
select benchmark_machine_type, benchmark_rw_mode,
       primary_clat_p50_ns / 1000.0 as latency_us
from fio
where valid_measurement
  and storage_target = 'local'
  and block_volume_performance_class = (select local_instance_comparison_block_performance_class from report_config)
  and benchmark_rw_mode = (select local_instance_rw_mode from report_config)
  and io_engine = (select default_io_engine from report_config)
  and block_size = (select iops_latency_block_size from report_config)
  and iodepth = (select iops_latency_iodepth from report_config)
  and numjobs = (select default_numjobs from report_config)
")
metric_box(
  latency_instance_local_p50,
  x = "benchmark_machine_type",
  y = "latency_us",
  fill = "benchmark_machine_type",
  title = "Local storage P50 latency by instance type",
  ylab = "P50 latency (us)",
  ncol = 1
)
```

## Block Storage Performance Class Impact

Filter values: see the resolved report configuration table above. Expand the collapsed code block to inspect the exact SQL predicate for this plot.

### P99

```{r latency-perf-class, results='asis', fig.width=12, fig.height=7}
render_performance_class_plots(
  "primary_clat_p99_ns / 1000.0",
  "P99 latency (us)",
  "P99 latency",
  "iops_latency_block_size",
  "iops_latency_iodepth",
  heading_level = 4
)
```

### P50

```{r latency-perf-class-p50, results='asis', fig.width=12, fig.height=7}
render_performance_class_plots(
  "primary_clat_p50_ns / 1000.0",
  "P50 latency (us)",
  "P50 latency",
  "iops_latency_block_size",
  "iops_latency_iodepth",
  heading_level = 4
)
```

## Execution Configuration Impact

The execution configuration combines `io_engine`, `iodepth`, and `numjobs`. This makes concurrency differences explicit instead of attributing them to the I/O engine alone.

Filter values: see the resolved report configuration table above. Expand the collapsed code block to inspect the exact SQL predicate for this plot.

### P99

```{r latency-execution-config, fig.width=12, fig.height=7}
latency_execution_config <- sql("
select concat(io_engine, ' / q', cast(iodepth as varchar), ' / jobs=', cast(numjobs as varchar)) as execution_config,
       benchmark_rw_mode,
       primary_clat_p99_ns / 1000.0 as latency_us
from fio
where valid_measurement
  and benchmark_machine_type = (select reference_machine_type from report_config)
  and block_volume_performance_class = (select reference_block_performance_class from report_config)
  and storage_target = 'block'
  and block_size = (select iops_latency_block_size from report_config)
order by case when io_engine = 'io_uring' then 1 else 2 end, iodepth, numjobs
")
metric_box(
  latency_execution_config,
  x = "execution_config",
  y = "latency_us",
  fill = "execution_config",
  title = "P99 latency by execution configuration",
  ylab = "P99 latency (us)"
)
```

#### io_uring Queue Depth

This diagnostic fixes `io_engine` and `numjobs`, then compares `iodepth`.

```{r latency-iouring-iodepth, fig.width=12, fig.height=7}
latency_iouring_iodepth <- sql("
select concat('q', cast(iodepth as varchar)) as iodepth_config, benchmark_rw_mode,
       primary_clat_p99_ns / 1000.0 as latency_us
from fio
where valid_measurement
  and benchmark_machine_type = (select reference_machine_type from report_config)
  and block_volume_performance_class = (select reference_block_performance_class from report_config)
  and storage_target = 'block'
  and block_size = (select iops_latency_block_size from report_config)
  and io_engine = (select default_io_engine from report_config)
  and numjobs = (select default_numjobs from report_config)
")
metric_box(
  latency_iouring_iodepth,
  x = "iodepth_config",
  y = "latency_us",
  fill = "iodepth_config",
  title = "io_uring P99 latency by queue depth",
  ylab = "P99 latency (us)"
)
```

#### psync Worker Count

This diagnostic fixes `io_engine = psync` and `iodepth`, then compares `numjobs`.

```{r latency-psync-numjobs, fig.width=12, fig.height=7}
latency_psync_numjobs <- sql("
select concat('jobs=', cast(numjobs as varchar)) as numjobs_config, benchmark_rw_mode,
       primary_clat_p99_ns / 1000.0 as latency_us
from fio
where valid_measurement
  and benchmark_machine_type = (select reference_machine_type from report_config)
  and block_volume_performance_class = (select reference_block_performance_class from report_config)
  and storage_target = 'block'
  and block_size = (select iops_latency_block_size from report_config)
  and io_engine = 'psync'
  and iodepth = (select psync_iodepth from report_config)
")
metric_box(
  latency_psync_numjobs,
  x = "numjobs_config",
  y = "latency_us",
  fill = "numjobs_config",
  title = "psync P99 latency by worker count",
  ylab = "P99 latency (us)"
)
```

### P50

```{r latency-execution-config-p50, fig.width=12, fig.height=7}
latency_execution_config_p50 <- sql("
select concat(io_engine, ' / q', cast(iodepth as varchar), ' / jobs=', cast(numjobs as varchar)) as execution_config,
       benchmark_rw_mode,
       primary_clat_p50_ns / 1000.0 as latency_us
from fio
where valid_measurement
  and benchmark_machine_type = (select reference_machine_type from report_config)
  and block_volume_performance_class = (select reference_block_performance_class from report_config)
  and storage_target = 'block'
  and block_size = (select iops_latency_block_size from report_config)
order by case when io_engine = 'io_uring' then 1 else 2 end, iodepth, numjobs
")
metric_box(
  latency_execution_config_p50,
  x = "execution_config",
  y = "latency_us",
  fill = "execution_config",
  title = "P50 latency by execution configuration",
  ylab = "P50 latency (us)"
)
```

#### io_uring Queue Depth

```{r latency-iouring-iodepth-p50, fig.width=12, fig.height=7}
latency_iouring_iodepth_p50 <- sql("
select concat('q', cast(iodepth as varchar)) as iodepth_config, benchmark_rw_mode,
       primary_clat_p50_ns / 1000.0 as latency_us
from fio
where valid_measurement
  and benchmark_machine_type = (select reference_machine_type from report_config)
  and block_volume_performance_class = (select reference_block_performance_class from report_config)
  and storage_target = 'block'
  and block_size = (select iops_latency_block_size from report_config)
  and io_engine = (select default_io_engine from report_config)
  and numjobs = (select default_numjobs from report_config)
")
metric_box(
  latency_iouring_iodepth_p50,
  x = "iodepth_config",
  y = "latency_us",
  fill = "iodepth_config",
  title = "io_uring P50 latency by queue depth",
  ylab = "P50 latency (us)"
)
```

#### psync Worker Count

```{r latency-psync-numjobs-p50, fig.width=12, fig.height=7}
latency_psync_numjobs_p50 <- sql("
select concat('jobs=', cast(numjobs as varchar)) as numjobs_config, benchmark_rw_mode,
       primary_clat_p50_ns / 1000.0 as latency_us
from fio
where valid_measurement
  and benchmark_machine_type = (select reference_machine_type from report_config)
  and block_volume_performance_class = (select reference_block_performance_class from report_config)
  and storage_target = 'block'
  and block_size = (select iops_latency_block_size from report_config)
  and io_engine = 'psync'
  and iodepth = (select psync_iodepth from report_config)
")
metric_box(
  latency_psync_numjobs_p50,
  x = "numjobs_config",
  y = "latency_us",
  fill = "numjobs_config",
  title = "psync P50 latency by worker count",
  ylab = "P50 latency (us)"
)
```

## Block Size Impact

The following plots make the configured block-size effect visible. Queue depth is matched per block size using the resolved `block_size_comparison` mapping.

### Block Storage

Filter values: see the resolved report configuration table above. Expand the collapsed code block to inspect the exact SQL predicate for this plot.

#### P99

```{r latency-block-size, fig.width=12, fig.height=7}
latency_block_size <- sql("
select block_size, benchmark_rw_mode,
       primary_clat_p99_ns / 1000.0 as latency_us
from fio
where valid_measurement
  and benchmark_machine_type = (select reference_machine_type from report_config)
  and block_volume_performance_class = (select reference_block_performance_class from report_config)
  and storage_target = 'block'
  and io_engine = (select default_io_engine from report_config)
  and numjobs = (select default_numjobs from report_config)
  and exists (
    select 1 from report_block_size_comparison comparison
    where comparison.block_size = fio.block_size
      and comparison.iodepth = fio.iodepth
  )
")
metric_box(
  latency_block_size,
  x = "block_size",
  y = "latency_us",
  fill = "block_size",
  title = "Block storage P99 latency by block size",
  ylab = "P99 latency (us)"
)
```

#### P50

```{r latency-block-size-p50, fig.width=12, fig.height=7}
latency_block_size_p50 <- sql("
select block_size, benchmark_rw_mode,
       primary_clat_p50_ns / 1000.0 as latency_us
from fio
where valid_measurement
  and benchmark_machine_type = (select reference_machine_type from report_config)
  and block_volume_performance_class = (select reference_block_performance_class from report_config)
  and storage_target = 'block'
  and io_engine = (select default_io_engine from report_config)
  and numjobs = (select default_numjobs from report_config)
  and exists (
    select 1 from report_block_size_comparison comparison
    where comparison.block_size = fio.block_size
      and comparison.iodepth = fio.iodepth
  )
")
metric_box(
  latency_block_size_p50,
  x = "block_size",
  y = "latency_us",
  fill = "block_size",
  title = "Block storage P50 latency by block size",
  ylab = "P50 latency (us)"
)
```

### Local Storage

Filter values: see the resolved report configuration table above. Expand the collapsed code block to inspect the exact SQL predicate for this plot.

#### P99

```{r latency-block-size-local, fig.width=12, fig.height=7}
latency_block_size_local <- sql("
select block_size, benchmark_rw_mode,
       primary_clat_p99_ns / 1000.0 as latency_us
from fio
where valid_measurement
  and benchmark_machine_type = (select reference_machine_type from report_config)
  and block_volume_performance_class = (select reference_block_performance_class from report_config)
  and storage_target = 'local'
  and io_engine = (select default_io_engine from report_config)
  and numjobs = (select default_numjobs from report_config)
  and exists (
    select 1 from report_block_size_comparison comparison
    where comparison.block_size = fio.block_size
      and comparison.iodepth = fio.iodepth
  )
")
metric_box(
  latency_block_size_local,
  x = "block_size",
  y = "latency_us",
  fill = "block_size",
  title = "Local storage P99 latency by block size",
  ylab = "P99 latency (us)"
)
```

#### P50

```{r latency-block-size-local-p50, fig.width=12, fig.height=7}
latency_block_size_local_p50 <- sql("
select block_size, benchmark_rw_mode,
       primary_clat_p50_ns / 1000.0 as latency_us
from fio
where valid_measurement
  and benchmark_machine_type = (select reference_machine_type from report_config)
  and block_volume_performance_class = (select reference_block_performance_class from report_config)
  and storage_target = 'local'
  and io_engine = (select default_io_engine from report_config)
  and numjobs = (select default_numjobs from report_config)
  and exists (
    select 1 from report_block_size_comparison comparison
    where comparison.block_size = fio.block_size
      and comparison.iodepth = fio.iodepth
  )
")
metric_box(
  latency_block_size_local_p50,
  x = "block_size",
  y = "latency_us",
  fill = "block_size",
  title = "Local storage P50 latency by block size",
  ylab = "P50 latency (us)"
)
```

## Storage Target Impact

Filter values: see the resolved report configuration table above. Expand the collapsed code block to inspect the exact SQL predicate for this plot.

### P99

```{r latency-target, fig.width=12, fig.height=7}
latency_target <- sql("
select storage_target, benchmark_rw_mode,
       primary_clat_p99_ns / 1000.0 as latency_us
from fio
where valid_measurement
  and benchmark_machine_type = (select reference_machine_type from report_config)
  and block_volume_performance_class = (select reference_block_performance_class from report_config)
  and storage_target in ('local', 'block')
  and io_engine = (select default_io_engine from report_config)
  and block_size = (select iops_latency_block_size from report_config)
  and iodepth = (select iops_latency_iodepth from report_config)
  and numjobs = (select default_numjobs from report_config)
")
metric_box(
  latency_target,
  x = "storage_target",
  y = "latency_us",
  fill = "storage_target",
  title = "P99 latency by storage target",
  ylab = "P99 latency (us)"
)
```

### P50

```{r latency-target-p50, fig.width=12, fig.height=7}
latency_target_p50 <- sql("
select storage_target, benchmark_rw_mode,
       primary_clat_p50_ns / 1000.0 as latency_us
from fio
where valid_measurement
  and benchmark_machine_type = (select reference_machine_type from report_config)
  and block_volume_performance_class = (select reference_block_performance_class from report_config)
  and storage_target in ('local', 'block')
  and io_engine = (select default_io_engine from report_config)
  and block_size = (select iops_latency_block_size from report_config)
  and iodepth = (select iops_latency_iodepth from report_config)
  and numjobs = (select default_numjobs from report_config)
")
metric_box(
  latency_target_p50,
  x = "storage_target",
  y = "latency_us",
  fill = "storage_target",
  title = "P50 latency by storage target",
  ylab = "P50 latency (us)"
)
```

```{r latency-summary}
latency_summary <- sql("
select benchmark_machine_type, block_volume_performance_class, storage_target,
       benchmark_rw_mode, io_engine, block_size, iodepth, numjobs,
       iodepth * numjobs as effective_concurrency,
       round(median(primary_clat_mean_ns) / 1000.0, 2) as median_avg_us,
       round(median(primary_clat_p50_ns) / 1000.0, 2) as median_p50_us,
       round(median(primary_clat_p99_ns) / 1000.0, 2) as median_p99_us,
       round(median(primary_clat_p999_ns) / 1000.0, 2) as median_p999_us,
       count(*) as repetitions
from fio
where valid_measurement
  and block_size = (select iops_latency_block_size from report_config)
group by 1, 2, 3, 4, 5, 6, 7, 8, 9
order by 1, 2, 3, 4, 5, 6, 7, 8, 9
")
kable(latency_summary, caption = sprintf("Latency summary for %s measurements", report_config$iops_latency_block_size))
```

# OS Tuning Coverage

The current dataset does not contain paired `standard` and `tuned` storage runs, so there is no meaningful OS tuning impact plot yet.

```{r tuning-coverage}
tuning_coverage <- sql("
select os_tuning, count(*) as repetitions
from fio
where valid_measurement
group by 1
order by 1
")
kable(tuning_coverage, caption = "OS tuning coverage in valid fio repetitions")
```

# Diagnostics

```{r failures}
if (nrow(sql("select * from failures")) == 0) {
  cat("No failed fio runs were captured.")
} else {
  failure_table <- sql("
  select run_id, scenario_name, benchmark_name, storage_target, repetition, fio_error, failure_reason
  from failures
  order by run_id, scenario_name, benchmark_name, storage_target, repetition
  ")
  kable(failure_table, caption = "Failed fio repetitions")
}
```

```{r local-target-coverage}
local_summary <- sql("
select benchmark_machine_type, block_volume_performance_class, storage_target,
       benchmark_rw_mode, io_engine, block_size, iodepth, numjobs,
       iodepth * numjobs as effective_concurrency,
       sum(case when valid_measurement then 1 else 0 end) as valid_repetitions,
       sum(case when not valid_measurement then 1 else 0 end) as invalid_repetitions
from fio
where storage_target = 'local'
group by 1, 2, 3, 4, 5, 6, 7, 8, 9
order by 1, 2, 3, 4, 5, 6, 7, 8, 9
")
if (nrow(local_summary) == 0) {
  cat("No local-target measurements were parsed.")
} else {
  kable(local_summary, caption = "Local-target coverage")
}
```
