---
title: "Storage Benchmark Analysis"
params:
  result_id: "all"
  note: null
output:
  html_document:
    toc: true
    toc_depth: 2
    code_folding: hide
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE, warning = FALSE, message = FALSE, fig.width = 12, fig.height = 7)

rmd_dir <- dirname(normalizePath(knitr::current_input(dir = TRUE)))
repo_root <- normalizePath(file.path(rmd_dir, "..", ".."))

source(file.path(repo_root, "analysis", "storage", "prelude.r"))
options(scipen = 999)

result_id <- params$result_id
results_dir <- file.path(repo_root, "analysis", "storage", result_id)

required_csvs <- c(
  "storage_scenarios.csv",
  "storage_benchmarks.csv",
  "storage_fio.csv",
  "storage_failures.csv"
)

if (!all(file.exists(file.path(results_dir, required_csvs)))) {
  stop(sprintf("Missing storage CSVs in %s. Run analysis/storage/build_csv.R first.", results_dir))
}

csv_sql_path <- function(name) {
  gsub("'", "''", normalizePath(file.path(results_dir, name), mustWork = TRUE), fixed = TRUE)
}

sql("select 1")
con <- duckdbcons[[":memory:"]]
DBI::dbExecute(con, "drop table if exists scenarios")
DBI::dbExecute(con, "drop table if exists benchmarks")
DBI::dbExecute(con, "drop table if exists fio")
DBI::dbExecute(con, "drop table if exists failures")
DBI::dbExecute(con, sprintf("create table scenarios as select * from read_csv_auto('%s')", csv_sql_path("storage_scenarios.csv")))
DBI::dbExecute(con, sprintf("create table benchmarks as select * from read_csv_auto('%s')", csv_sql_path("storage_benchmarks.csv")))
DBI::dbExecute(con, sprintf("create table fio as select * from read_csv_auto('%s')", csv_sql_path("storage_fio.csv")))
DBI::dbExecute(con, sprintf("create table failures as select * from read_csv_auto('%s')", csv_sql_path("storage_failures.csv")))

machine_levels <- c("g2a.8d", "g2a.30d", "g2a.120d")
workload_levels <- c("randread", "randwrite", "read", "write")
engine_levels <- c("psync", "io_uring")
block_size_levels <- c("4k", "128k")
target_levels <- c("local", "block")
perf_class_order <- sql("
select distinct block_volume_performance_class
from scenarios
where block_volume_performance_class is not null
order by block_volume_performance_class
")$block_volume_performance_class
perf_class_order <- perf_class_order[order(as.integer(sub(".*perf([0-9]+).*", "\\1", perf_class_order)))]

wrap_subtitle <- function(text, width = 78) {
  if (is.null(text) || !nzchar(text)) return(NULL)
  paste(strwrap(text, width = width), collapse = "\n")
}

apply_factor_levels <- function(df) {
  if ("benchmark_machine_type" %in% names(df)) {
    df$benchmark_machine_type <- factor(df$benchmark_machine_type, levels = machine_levels)
  }
  if ("benchmark_rw_mode" %in% names(df)) {
    df$benchmark_rw_mode <- factor(df$benchmark_rw_mode, levels = workload_levels)
  }
  if ("io_engine" %in% names(df)) {
    df$io_engine <- factor(df$io_engine, levels = engine_levels)
  }
  if ("block_size" %in% names(df)) {
    df$block_size <- factor(df$block_size, levels = block_size_levels)
  }
  if ("storage_target" %in% names(df)) {
    df$storage_target <- factor(df$storage_target, levels = target_levels)
  }
  if ("block_volume_performance_class" %in% names(df)) {
    df$block_volume_performance_class <- factor(df$block_volume_performance_class, levels = perf_class_order)
  }
  if ("latency_metric" %in% names(df)) {
    df$latency_metric <- factor(df$latency_metric, levels = c("avg", "p50", "p99", "p99.9"))
  }
  df
}

metric_box <- function(df, x, y, fill = NULL, facet = "benchmark_rw_mode", title = NULL,
                       subtitle = NULL, ylab = NULL, ncol = 2, y_zero = TRUE) {
  if (nrow(df) == 0) return(show_no_data_plot("No data for this comparison."))
  df <- apply_factor_levels(df)
  mapping <- if (is.null(fill)) {
    aes(x = .data[[x]], y = .data[[y]])
  } else {
    aes(x = .data[[x]], y = .data[[y]], fill = .data[[fill]])
  }
  p <- ggplot(df, mapping) +
    geom_boxplot(outlier.shape = NA, alpha = 0.72) +
    geom_jitter(width = 0.12, alpha = 0.55, size = 1.5) +
    labs(title = title, subtitle = wrap_subtitle(subtitle), x = NULL, y = ylab, fill = NULL) +
    base_plot_theme()

  if (y_zero) {
    p <- p + scale_y_continuous(labels = comma, limits = c(0, NA), expand = expansion(mult = c(0, 0.06)))
  } else {
    p <- p + scale_y_continuous(labels = comma, expand = expansion(mult = c(0.02, 0.06)))
  }

  if (!is.null(facet)) {
    p <- p + facet_wrap(stats::as.formula(paste("~", facet)), ncol = ncol, scales = "fixed")
  }

  p + guides(fill = "none")
}

metric_summary <- function(df, group_cols, metric_col) {
  if (nrow(df) == 0) return(df)
  aggregate(
    df[[metric_col]],
    df[group_cols],
    function(x) c(median = median(x, na.rm = TRUE), min = min(x, na.rm = TRUE), max = max(x, na.rm = TRUE), n = length(x))
  )
}

validate_rows <- sql("
select
  count(*) as fio_rows,
  sum(case when valid_measurement then 1 else 0 end) as valid_rows,
  sum(case when not valid_measurement then 1 else 0 end) as invalid_rows,
  count(distinct run_id) as runs
from fio
")
```

This report analyzes storage benchmark results from `r result_id`.

```{r note, results='asis', echo=FALSE}
if (!is.null(params$note) && nzchar(params$note)) {
  cat(sprintf("> %s\n\n", params$note))
}
```

# Overview

The report intentionally avoids using `benchmark_name` as a plot facet for impact analysis. The benchmark name is a derived label that includes dimensions such as block size and I/O engine. The plots below compare one dimension at a time while fixing the other relevant dimensions in SQL.

Throughput plots focus on `128k`, `io_uring`, and `iodepth = 16` unless the plot explicitly compares block size. IOPS and latency plots focus on `4k`, `io_uring`, and `iodepth = 32` unless the plot explicitly compares I/O engine. The `psync/4k` measurements use `iodepth = 1`. This avoids mixing the latency-oriented `psync_4k` workloads into throughput comparisons and avoids mixing `128k` workloads into latency comparisons.

```{r coverage-counts}
coverage_counts <- sql("
select
  (select count(*) from scenarios) as scenarios,
  (select count(*) from benchmarks) as benchmark_rows,
  (select count(*) from fio) as fio_rows,
  (select count(*) from failures) as failures,
  (select sum(case when valid_measurement then 1 else 0 end) from fio) as valid_fio_rows
")
kable(coverage_counts, caption = "Parsed storage benchmark data")
```

```{r filter-policy, echo=FALSE}
filter_policy <- data.frame(
  section = c("Throughput", "Throughput block-size impact", "IOPS", "Latency"),
  default_filter = c(
    "block_size = 128k, io_engine = io_uring, iodepth = 16, psync omitted",
    "io_engine = io_uring, compares block_size on x-axis; 4k uses iodepth = 32 and 128k uses iodepth = 16",
    "block_size = 4k, io_engine fixed unless comparing I/O engine; io_uring uses iodepth = 32 and psync uses iodepth = 1",
    "block_size = 4k, io_uring uses iodepth = 32, 128k omitted except diagnostic block-size plots"
  )
)
kable(filter_policy, caption = "Default filtering policy")
```

```{r scenario-table}
scenario_table <- sql("
select run_id, scenario_name, benchmark_machine_type, benchmark_availability_zone,
       os_tuning, access_mode, storage_targets_raw, block_volume_performance_class
from scenarios
order by run_id, scenario_name
")
kable(scenario_table, caption = "Scenario coverage")
```

```{r dimension-coverage}
dimension_coverage <- sql("
select benchmark_machine_type, block_volume_performance_class, storage_target,
       benchmark_rw_mode, io_engine, block_size,
       sum(case when valid_measurement then 1 else 0 end) as valid_repetitions
from fio
group by 1, 2, 3, 4, 5, 6
order by 1, 2, 3, 4, 5, 6
")
kable(dimension_coverage, caption = "Coverage by explicit analysis dimensions")
```

# Throughput

Throughput is reported as MiB/s using `primary_bw_bytes_per_sec`. The main throughput comparisons fix `block_size = 128k`, `io_engine = io_uring`, and `iodepth = 16`.

## Instance Type Impact

### Block Storage

Filter used: `storage_target = block`, `block_volume_performance_class = storage_premium_perf12`, `io_engine = io_uring`, `block_size = 128k`, `iodepth = 16`. This keeps the block-volume class constant while comparing instance types. The `g2a.30d` run is not present in this plot because the current dataset does not contain comparable `128k/io_uring` measurements for that instance type.

```{r throughput-instance, fig.width=12, fig.height=7}
throughput_instance <- sql("
select benchmark_machine_type, benchmark_rw_mode,
       primary_bw_bytes_per_sec / 1024.0 / 1024.0 as bw_mib_per_sec
from fio
where valid_measurement
  and storage_target = 'block'
  and block_volume_performance_class = 'storage_premium_perf12'
  and io_engine = 'io_uring'
  and block_size = '128k'
")
metric_box(
  throughput_instance,
  x = "benchmark_machine_type",
  y = "bw_mib_per_sec",
  fill = "benchmark_machine_type",
  title = "Block storage throughput by instance type",
  ylab = "Throughput (MiB/s)"
)
```

### Local Storage

Filter used: `storage_target = local`, `block_volume_performance_class = storage_premium_perf6`, `benchmark_rw_mode = randread`, `io_engine = io_uring`, `block_size = 4k`, `iodepth = 32`. This is the only local subset that currently compares more than one instance type. The local `g2a.120d` full matrix exists, but `g2a.30d` only has this local benchmark and `g2a.8d` has no local measurements.

```{r throughput-instance-local, fig.width=12, fig.height=5}
throughput_instance_local <- sql("
select benchmark_machine_type, benchmark_rw_mode,
       primary_bw_bytes_per_sec / 1024.0 / 1024.0 as bw_mib_per_sec
from fio
where valid_measurement
  and storage_target = 'local'
  and block_volume_performance_class = 'storage_premium_perf6'
  and benchmark_rw_mode = 'randread'
  and io_engine = 'io_uring'
  and block_size = '4k'
")
metric_box(
  throughput_instance_local,
  x = "benchmark_machine_type",
  y = "bw_mib_per_sec",
  fill = "benchmark_machine_type",
  title = "Local storage throughput by instance type",
  ylab = "Throughput (MiB/s)",
  ncol = 1
)
```

## Block Storage Performance Class Impact

Filter used: `storage_target = block`, `io_engine = io_uring`, `block_size = 128k`, `iodepth = 16`. The comparison is split by instance type because available performance classes differ by instance. Subsections with only one performance class are kept so newly added measurements appear without changing the report structure.

### g2a.8d

```{r throughput-perf-class-8d, fig.width=12, fig.height=7}
throughput_perf_class_8d <- sql("
select block_volume_performance_class, benchmark_rw_mode,
       primary_bw_bytes_per_sec / 1024.0 / 1024.0 as bw_mib_per_sec
from fio
where valid_measurement
  and benchmark_machine_type = 'g2a.8d'
  and storage_target = 'block'
  and io_engine = 'io_uring'
  and block_size = '128k'
  and block_volume_performance_class is not null
")
metric_box(
  throughput_perf_class_8d,
  x = "block_volume_performance_class",
  y = "bw_mib_per_sec",
  fill = "block_volume_performance_class",
  title = "g2a.8d block storage throughput by performance class",
  ylab = "Throughput (MiB/s)"
)
```

### g2a.30d

```{r throughput-perf-class-30d, fig.width=12, fig.height=7}
throughput_perf_class_30d <- sql("
select block_volume_performance_class, benchmark_rw_mode,
       primary_bw_bytes_per_sec / 1024.0 / 1024.0 as bw_mib_per_sec
from fio
where valid_measurement
  and benchmark_machine_type = 'g2a.30d'
  and storage_target = 'block'
  and io_engine = 'io_uring'
  and block_size = '128k'
  and block_volume_performance_class is not null
")
metric_box(
  throughput_perf_class_30d,
  x = "block_volume_performance_class",
  y = "bw_mib_per_sec",
  fill = "block_volume_performance_class",
  title = "g2a.30d block storage throughput by performance class",
  ylab = "Throughput (MiB/s)"
)
```

### g2a.120d

```{r throughput-perf-class-120d, fig.width=12, fig.height=7}
throughput_perf_class_120d <- sql("
select block_volume_performance_class, benchmark_rw_mode,
       primary_bw_bytes_per_sec / 1024.0 / 1024.0 as bw_mib_per_sec
from fio
where valid_measurement
  and benchmark_machine_type = 'g2a.120d'
  and storage_target = 'block'
  and io_engine = 'io_uring'
  and block_size = '128k'
  and block_volume_performance_class is not null
")
metric_box(
  throughput_perf_class_120d,
  x = "block_volume_performance_class",
  y = "bw_mib_per_sec",
  fill = "block_volume_performance_class",
  title = "g2a.120d block storage throughput by performance class",
  ylab = "Throughput (MiB/s)"
)
```

## Storage Target Impact

Filter used: `benchmark_machine_type = g2a.120d`, `block_volume_performance_class = storage_premium_perf29`, `io_engine = io_uring`, `block_size = 128k`, `iodepth = 16`. The highest available performance class is used so the local-vs-block comparison is not dominated by a deliberately low block-volume class.

```{r throughput-target, fig.width=12, fig.height=7}
throughput_target <- sql("
select storage_target, benchmark_rw_mode,
       primary_bw_bytes_per_sec / 1024.0 / 1024.0 as bw_mib_per_sec
from fio
where valid_measurement
  and benchmark_machine_type = 'g2a.120d'
  and block_volume_performance_class = 'storage_premium_perf29'
  and storage_target in ('local', 'block')
  and io_engine = 'io_uring'
  and block_size = '128k'
")
metric_box(
  throughput_target,
  x = "storage_target",
  y = "bw_mib_per_sec",
  fill = "storage_target",
  title = "Throughput by storage target",
  ylab = "Throughput (MiB/s)"
)
```

## Block Size Impact

### Block Storage

Filter used: `benchmark_machine_type = g2a.120d`, `block_volume_performance_class = storage_premium_perf29`, `storage_target = block`, `io_engine = io_uring`. Block size is the compared dimension and is therefore shown on the x-axis. Note that the `4k` measurements use `iodepth = 32`, while the `128k` measurements use `iodepth = 16`.

```{r throughput-block-size, fig.width=12, fig.height=7}
throughput_block_size <- sql("
select block_size, benchmark_rw_mode,
       primary_bw_bytes_per_sec / 1024.0 / 1024.0 as bw_mib_per_sec
from fio
where valid_measurement
  and benchmark_machine_type = 'g2a.120d'
  and block_volume_performance_class = 'storage_premium_perf29'
  and storage_target = 'block'
  and io_engine = 'io_uring'
  and block_size in ('4k', '128k')
")
metric_box(
  throughput_block_size,
  x = "block_size",
  y = "bw_mib_per_sec",
  fill = "block_size",
  title = "Throughput by block size",
  ylab = "Throughput (MiB/s)"
)
```

### Local Storage

Filter used: `benchmark_machine_type = g2a.120d`, `block_volume_performance_class = storage_premium_perf29`, `storage_target = local`, `io_engine = io_uring`. Block size is the compared dimension and is therefore shown on the x-axis. Note that the `4k` measurements use `iodepth = 32`, while the `128k` measurements use `iodepth = 16`.

```{r throughput-block-size-local, fig.width=12, fig.height=7}
throughput_block_size_local <- sql("
select block_size, benchmark_rw_mode,
       primary_bw_bytes_per_sec / 1024.0 / 1024.0 as bw_mib_per_sec
from fio
where valid_measurement
  and benchmark_machine_type = 'g2a.120d'
  and block_volume_performance_class = 'storage_premium_perf29'
  and storage_target = 'local'
  and io_engine = 'io_uring'
  and block_size in ('4k', '128k')
")
metric_box(
  throughput_block_size_local,
  x = "block_size",
  y = "bw_mib_per_sec",
  fill = "block_size",
  title = "Local storage throughput by block size",
  ylab = "Throughput (MiB/s)"
)
```

```{r throughput-summary}
throughput_summary <- sql("
select benchmark_machine_type, block_volume_performance_class, storage_target,
       benchmark_rw_mode, io_engine, block_size, iodepth,
       round(median(primary_bw_bytes_per_sec) / 1024.0 / 1024.0, 2) as median_mib_per_sec,
       round(avg(primary_bw_bytes_per_sec) / 1024.0 / 1024.0, 2) as avg_mib_per_sec,
       count(*) as repetitions
from fio
where valid_measurement
  and block_size = '128k'
  and io_engine = 'io_uring'
group by 1, 2, 3, 4, 5, 6, 7
order by 1, 2, 3, 4, 5, 6, 7
")
kable(throughput_summary, caption = "Throughput summary for io_uring 128k measurements")
```

# IOPS

IOPS is reported using `primary_iops`. The main IOPS comparisons fix `block_size = 4k`; for `io_uring` this means `iodepth = 32`. The `psync/4k` engine comparison uses `iodepth = 1`.

## Instance Type Impact

### Block Storage

Filter used: `storage_target = block`, `block_volume_performance_class = storage_premium_perf12`, `io_engine = io_uring`, `block_size = 4k`, `iodepth = 32`. Instance type is shown on the x-axis.

```{r iops-instance, fig.width=12, fig.height=7}
iops_instance <- sql("
select benchmark_machine_type, benchmark_rw_mode, primary_iops as iops
from fio
where valid_measurement
  and storage_target = 'block'
  and block_volume_performance_class = 'storage_premium_perf12'
  and io_engine = 'io_uring'
  and block_size = '4k'
")
metric_box(
  iops_instance,
  x = "benchmark_machine_type",
  y = "iops",
  fill = "benchmark_machine_type",
  title = "Block storage IOPS by instance type",
  ylab = "IOPS"
)
```

### Local Storage

Filter used: `storage_target = local`, `block_volume_performance_class = storage_premium_perf6`, `benchmark_rw_mode = randread`, `io_engine = io_uring`, `block_size = 4k`, `iodepth = 32`. This is the only local subset that currently compares more than one instance type.

```{r iops-instance-local, fig.width=12, fig.height=5}
iops_instance_local <- sql("
select benchmark_machine_type, benchmark_rw_mode, primary_iops as iops
from fio
where valid_measurement
  and storage_target = 'local'
  and block_volume_performance_class = 'storage_premium_perf6'
  and benchmark_rw_mode = 'randread'
  and io_engine = 'io_uring'
  and block_size = '4k'
")
metric_box(
  iops_instance_local,
  x = "benchmark_machine_type",
  y = "iops",
  fill = "benchmark_machine_type",
  title = "Local storage IOPS by instance type",
  ylab = "IOPS",
  ncol = 1
)
```

## Block Storage Performance Class Impact

Filter used: `storage_target = block`, `io_engine = io_uring`, `block_size = 4k`, `iodepth = 32`. The comparison is split by instance type because available performance classes differ by instance. Subsections with only one performance class are kept so newly added measurements appear without changing the report structure.

### g2a.8d

```{r iops-perf-class-8d, fig.width=12, fig.height=7}
iops_perf_class_8d <- sql("
select block_volume_performance_class, benchmark_rw_mode, primary_iops as iops
from fio
where valid_measurement
  and benchmark_machine_type = 'g2a.8d'
  and storage_target = 'block'
  and io_engine = 'io_uring'
  and block_size = '4k'
  and block_volume_performance_class is not null
")
metric_box(
  iops_perf_class_8d,
  x = "block_volume_performance_class",
  y = "iops",
  fill = "block_volume_performance_class",
  title = "g2a.8d block storage IOPS by performance class",
  ylab = "IOPS"
)
```

### g2a.30d

```{r iops-perf-class-30d, fig.width=12, fig.height=7}
iops_perf_class_30d <- sql("
select block_volume_performance_class, benchmark_rw_mode, primary_iops as iops
from fio
where valid_measurement
  and benchmark_machine_type = 'g2a.30d'
  and storage_target = 'block'
  and io_engine = 'io_uring'
  and block_size = '4k'
  and block_volume_performance_class is not null
")
metric_box(
  iops_perf_class_30d,
  x = "block_volume_performance_class",
  y = "iops",
  fill = "block_volume_performance_class",
  title = "g2a.30d block storage IOPS by performance class",
  ylab = "IOPS"
)
```

### g2a.120d

```{r iops-perf-class-120d, fig.width=12, fig.height=7}
iops_perf_class_120d <- sql("
select block_volume_performance_class, benchmark_rw_mode, primary_iops as iops
from fio
where valid_measurement
  and benchmark_machine_type = 'g2a.120d'
  and storage_target = 'block'
  and io_engine = 'io_uring'
  and block_size = '4k'
  and block_volume_performance_class is not null
")
metric_box(
  iops_perf_class_120d,
  x = "block_volume_performance_class",
  y = "iops",
  fill = "block_volume_performance_class",
  title = "g2a.120d block storage IOPS by performance class",
  ylab = "IOPS"
)
```

## I/O Engine Impact

Filter used: `benchmark_machine_type = g2a.120d`, `block_volume_performance_class = storage_premium_perf29`, `storage_target = block`, `block_size = 4k`. I/O engine is the compared dimension and is shown on the x-axis. The `io_uring` measurements use `iodepth = 32`; the `psync` measurements use `iodepth = 1`.

```{r iops-engine, fig.width=12, fig.height=7}
iops_engine <- sql("
select io_engine, benchmark_rw_mode, primary_iops as iops
from fio
where valid_measurement
  and benchmark_machine_type = 'g2a.120d'
  and block_volume_performance_class = 'storage_premium_perf29'
  and storage_target = 'block'
  and block_size = '4k'
  and io_engine in ('psync', 'io_uring')
")
metric_box(
  iops_engine,
  x = "io_engine",
  y = "iops",
  fill = "io_engine",
  title = "IOPS by I/O engine",
  ylab = "IOPS"
)
```

## Block Size Impact

### Block Storage

Filter used: `benchmark_machine_type = g2a.120d`, `block_volume_performance_class = storage_premium_perf29`, `storage_target = block`, `io_engine = io_uring`. Block size is the compared dimension and is therefore shown on the x-axis. Note that the `4k` measurements use `iodepth = 32`, while the `128k` measurements use `iodepth = 16`.

```{r iops-block-size, fig.width=12, fig.height=7}
iops_block_size <- sql("
select block_size, benchmark_rw_mode, primary_iops as iops
from fio
where valid_measurement
  and benchmark_machine_type = 'g2a.120d'
  and block_volume_performance_class = 'storage_premium_perf29'
  and storage_target = 'block'
  and io_engine = 'io_uring'
  and block_size in ('4k', '128k')
")
metric_box(
  iops_block_size,
  x = "block_size",
  y = "iops",
  fill = "block_size",
  title = "Block storage IOPS by block size",
  ylab = "IOPS"
)
```

### Local Storage

Filter used: `benchmark_machine_type = g2a.120d`, `block_volume_performance_class = storage_premium_perf29`, `storage_target = local`, `io_engine = io_uring`. Block size is the compared dimension and is therefore shown on the x-axis. Note that the `4k` measurements use `iodepth = 32`, while the `128k` measurements use `iodepth = 16`.

```{r iops-block-size-local, fig.width=12, fig.height=7}
iops_block_size_local <- sql("
select block_size, benchmark_rw_mode, primary_iops as iops
from fio
where valid_measurement
  and benchmark_machine_type = 'g2a.120d'
  and block_volume_performance_class = 'storage_premium_perf29'
  and storage_target = 'local'
  and io_engine = 'io_uring'
  and block_size in ('4k', '128k')
")
metric_box(
  iops_block_size_local,
  x = "block_size",
  y = "iops",
  fill = "block_size",
  title = "Local storage IOPS by block size",
  ylab = "IOPS"
)
```

## Storage Target Impact

Filter used: `benchmark_machine_type = g2a.120d`, `block_volume_performance_class = storage_premium_perf29`, `io_engine = io_uring`, `block_size = 4k`, `iodepth = 32`.

```{r iops-target, fig.width=12, fig.height=7}
iops_target <- sql("
select storage_target, benchmark_rw_mode, primary_iops as iops
from fio
where valid_measurement
  and benchmark_machine_type = 'g2a.120d'
  and block_volume_performance_class = 'storage_premium_perf29'
  and storage_target in ('local', 'block')
  and io_engine = 'io_uring'
  and block_size = '4k'
")
metric_box(
  iops_target,
  x = "storage_target",
  y = "iops",
  fill = "storage_target",
  title = "IOPS by storage target",
  ylab = "IOPS"
)
```

```{r iops-summary}
iops_summary <- sql("
select benchmark_machine_type, block_volume_performance_class, storage_target,
       benchmark_rw_mode, io_engine, block_size, iodepth,
       round(median(primary_iops), 2) as median_iops,
       round(avg(primary_iops), 2) as avg_iops,
       count(*) as repetitions
from fio
where valid_measurement
  and block_size = '4k'
group by 1, 2, 3, 4, 5, 6, 7
order by 1, 2, 3, 4, 5, 6, 7
")
kable(iops_summary, caption = "IOPS summary for 4k measurements")
```

# Latency

Latency is reported in microseconds. Latency plots focus on `block_size = 4k`; for `io_uring` this means `iodepth = 32`. `128k` measurements use `iodepth = 16` and are intentionally excluded from most latency impact plots because they represent a different throughput-oriented workload.

## Latency Metric Overview

Filter used: `benchmark_machine_type = g2a.120d`, `block_volume_performance_class = storage_premium_perf29`, `storage_target = block`, `io_engine = io_uring`, `block_size = 4k`, `iodepth = 32`. This plot shows average, median, and tail latency for the same fixed workload subset.

```{r latency-metric-overview, fig.width=12, fig.height=7}
latency_metric_overview <- sql("
select benchmark_rw_mode, 'avg' as latency_metric, primary_clat_mean_ns / 1000.0 as latency_us
from fio
where valid_measurement
  and benchmark_machine_type = 'g2a.120d'
  and block_volume_performance_class = 'storage_premium_perf29'
  and storage_target = 'block'
  and io_engine = 'io_uring'
  and block_size = '4k'
union all
select benchmark_rw_mode, 'p50' as latency_metric, primary_clat_p50_ns / 1000.0 as latency_us
from fio
where valid_measurement
  and benchmark_machine_type = 'g2a.120d'
  and block_volume_performance_class = 'storage_premium_perf29'
  and storage_target = 'block'
  and io_engine = 'io_uring'
  and block_size = '4k'
union all
select benchmark_rw_mode, 'p99' as latency_metric, primary_clat_p99_ns / 1000.0 as latency_us
from fio
where valid_measurement
  and benchmark_machine_type = 'g2a.120d'
  and block_volume_performance_class = 'storage_premium_perf29'
  and storage_target = 'block'
  and io_engine = 'io_uring'
  and block_size = '4k'
union all
select benchmark_rw_mode, 'p99.9' as latency_metric, primary_clat_p999_ns / 1000.0 as latency_us
from fio
where valid_measurement
  and benchmark_machine_type = 'g2a.120d'
  and block_volume_performance_class = 'storage_premium_perf29'
  and storage_target = 'block'
  and io_engine = 'io_uring'
  and block_size = '4k'
")
metric_box(
  latency_metric_overview,
  x = "latency_metric",
  y = "latency_us",
  fill = "latency_metric",
  title = "Latency distribution by metric",
  ylab = "Latency (us)"
)
```

## Instance Type Impact

### Block Storage

Filter used: `storage_target = block`, `block_volume_performance_class = storage_premium_perf12`, `io_engine = io_uring`, `block_size = 4k`, `iodepth = 32`. Instance type is shown on the x-axis.

#### P99

```{r latency-instance, fig.width=12, fig.height=7}
latency_instance <- sql("
select benchmark_machine_type, benchmark_rw_mode,
       primary_clat_p99_ns / 1000.0 as latency_us
from fio
where valid_measurement
  and storage_target = 'block'
  and block_volume_performance_class = 'storage_premium_perf12'
  and io_engine = 'io_uring'
  and block_size = '4k'
")
metric_box(
  latency_instance,
  x = "benchmark_machine_type",
  y = "latency_us",
  fill = "benchmark_machine_type",
  title = "Block storage P99 latency by instance type",
  ylab = "P99 latency (us)"
)
```

#### P50

```{r latency-instance-p50, fig.width=12, fig.height=7}
latency_instance_p50 <- sql("
select benchmark_machine_type, benchmark_rw_mode,
       primary_clat_p50_ns / 1000.0 as latency_us
from fio
where valid_measurement
  and storage_target = 'block'
  and block_volume_performance_class = 'storage_premium_perf12'
  and io_engine = 'io_uring'
  and block_size = '4k'
")
metric_box(
  latency_instance_p50,
  x = "benchmark_machine_type",
  y = "latency_us",
  fill = "benchmark_machine_type",
  title = "Block storage P50 latency by instance type",
  ylab = "P50 latency (us)"
)
```

### Local Storage

Filter used: `storage_target = local`, `block_volume_performance_class = storage_premium_perf6`, `benchmark_rw_mode = randread`, `io_engine = io_uring`, `block_size = 4k`, `iodepth = 32`. This is the only local subset that currently compares more than one instance type.

#### P99

```{r latency-instance-local, fig.width=12, fig.height=5}
latency_instance_local <- sql("
select benchmark_machine_type, benchmark_rw_mode,
       primary_clat_p99_ns / 1000.0 as latency_us
from fio
where valid_measurement
  and storage_target = 'local'
  and block_volume_performance_class = 'storage_premium_perf6'
  and benchmark_rw_mode = 'randread'
  and io_engine = 'io_uring'
  and block_size = '4k'
")
metric_box(
  latency_instance_local,
  x = "benchmark_machine_type",
  y = "latency_us",
  fill = "benchmark_machine_type",
  title = "Local storage P99 latency by instance type",
  ylab = "P99 latency (us)",
  ncol = 1
)
```

#### P50

```{r latency-instance-local-p50, fig.width=12, fig.height=5}
latency_instance_local_p50 <- sql("
select benchmark_machine_type, benchmark_rw_mode,
       primary_clat_p50_ns / 1000.0 as latency_us
from fio
where valid_measurement
  and storage_target = 'local'
  and block_volume_performance_class = 'storage_premium_perf6'
  and benchmark_rw_mode = 'randread'
  and io_engine = 'io_uring'
  and block_size = '4k'
")
metric_box(
  latency_instance_local_p50,
  x = "benchmark_machine_type",
  y = "latency_us",
  fill = "benchmark_machine_type",
  title = "Local storage P50 latency by instance type",
  ylab = "P50 latency (us)",
  ncol = 1
)
```

## Block Storage Performance Class Impact

Filter used: `storage_target = block`, `io_engine = io_uring`, `block_size = 4k`, `iodepth = 32`. The comparison is split by instance type because available performance classes differ by instance. Subsections with only one performance class are kept so newly added measurements appear without changing the report structure.

### P99

#### g2a.8d

```{r latency-perf-class-8d, fig.width=12, fig.height=7}
latency_perf_class_8d <- sql("
select block_volume_performance_class, benchmark_rw_mode,
       primary_clat_p99_ns / 1000.0 as latency_us
from fio
where valid_measurement
  and benchmark_machine_type = 'g2a.8d'
  and storage_target = 'block'
  and io_engine = 'io_uring'
  and block_size = '4k'
  and block_volume_performance_class is not null
")
metric_box(
  latency_perf_class_8d,
  x = "block_volume_performance_class",
  y = "latency_us",
  fill = "block_volume_performance_class",
  title = "g2a.8d block storage P99 latency by performance class",
  ylab = "P99 latency (us)"
)
```

#### g2a.30d

```{r latency-perf-class-30d, fig.width=12, fig.height=7}
latency_perf_class_30d <- sql("
select block_volume_performance_class, benchmark_rw_mode,
       primary_clat_p99_ns / 1000.0 as latency_us
from fio
where valid_measurement
  and benchmark_machine_type = 'g2a.30d'
  and storage_target = 'block'
  and io_engine = 'io_uring'
  and block_size = '4k'
  and block_volume_performance_class is not null
")
metric_box(
  latency_perf_class_30d,
  x = "block_volume_performance_class",
  y = "latency_us",
  fill = "block_volume_performance_class",
  title = "g2a.30d block storage P99 latency by performance class",
  ylab = "P99 latency (us)"
)
```

#### g2a.120d

```{r latency-perf-class-120d, fig.width=12, fig.height=7}
latency_perf_class_120d <- sql("
select block_volume_performance_class, benchmark_rw_mode,
       primary_clat_p99_ns / 1000.0 as latency_us
from fio
where valid_measurement
  and benchmark_machine_type = 'g2a.120d'
  and storage_target = 'block'
  and io_engine = 'io_uring'
  and block_size = '4k'
  and block_volume_performance_class is not null
")
metric_box(
  latency_perf_class_120d,
  x = "block_volume_performance_class",
  y = "latency_us",
  fill = "block_volume_performance_class",
  title = "g2a.120d block storage P99 latency by performance class",
  ylab = "P99 latency (us)"
)
```

### P50

#### g2a.8d

```{r latency-perf-class-p50-8d, fig.width=12, fig.height=7}
latency_perf_class_p50_8d <- sql("
select block_volume_performance_class, benchmark_rw_mode,
       primary_clat_p50_ns / 1000.0 as latency_us
from fio
where valid_measurement
  and benchmark_machine_type = 'g2a.8d'
  and storage_target = 'block'
  and io_engine = 'io_uring'
  and block_size = '4k'
  and block_volume_performance_class is not null
")
metric_box(
  latency_perf_class_p50_8d,
  x = "block_volume_performance_class",
  y = "latency_us",
  fill = "block_volume_performance_class",
  title = "g2a.8d block storage P50 latency by performance class",
  ylab = "P50 latency (us)"
)
```

#### g2a.30d

```{r latency-perf-class-p50-30d, fig.width=12, fig.height=7}
latency_perf_class_p50_30d <- sql("
select block_volume_performance_class, benchmark_rw_mode,
       primary_clat_p50_ns / 1000.0 as latency_us
from fio
where valid_measurement
  and benchmark_machine_type = 'g2a.30d'
  and storage_target = 'block'
  and io_engine = 'io_uring'
  and block_size = '4k'
  and block_volume_performance_class is not null
")
metric_box(
  latency_perf_class_p50_30d,
  x = "block_volume_performance_class",
  y = "latency_us",
  fill = "block_volume_performance_class",
  title = "g2a.30d block storage P50 latency by performance class",
  ylab = "P50 latency (us)"
)
```

#### g2a.120d

```{r latency-perf-class-p50-120d, fig.width=12, fig.height=7}
latency_perf_class_p50_120d <- sql("
select block_volume_performance_class, benchmark_rw_mode,
       primary_clat_p50_ns / 1000.0 as latency_us
from fio
where valid_measurement
  and benchmark_machine_type = 'g2a.120d'
  and storage_target = 'block'
  and io_engine = 'io_uring'
  and block_size = '4k'
  and block_volume_performance_class is not null
")
metric_box(
  latency_perf_class_p50_120d,
  x = "block_volume_performance_class",
  y = "latency_us",
  fill = "block_volume_performance_class",
  title = "g2a.120d block storage P50 latency by performance class",
  ylab = "P50 latency (us)"
)
```

## I/O Engine Impact

Filter used: `benchmark_machine_type = g2a.120d`, `block_volume_performance_class = storage_premium_perf29`, `storage_target = block`, `block_size = 4k`. The `io_uring` measurements use `iodepth = 32`; the `psync` measurements use `iodepth = 1`.

### P99

```{r latency-engine, fig.width=12, fig.height=7}
latency_engine <- sql("
select io_engine, benchmark_rw_mode,
       primary_clat_p99_ns / 1000.0 as latency_us
from fio
where valid_measurement
  and benchmark_machine_type = 'g2a.120d'
  and block_volume_performance_class = 'storage_premium_perf29'
  and storage_target = 'block'
  and block_size = '4k'
  and io_engine in ('psync', 'io_uring')
")
metric_box(
  latency_engine,
  x = "io_engine",
  y = "latency_us",
  fill = "io_engine",
  title = "P99 latency by I/O engine",
  ylab = "P99 latency (us)"
)
```

### P50

```{r latency-engine-p50, fig.width=12, fig.height=7}
latency_engine_p50 <- sql("
select io_engine, benchmark_rw_mode,
       primary_clat_p50_ns / 1000.0 as latency_us
from fio
where valid_measurement
  and benchmark_machine_type = 'g2a.120d'
  and block_volume_performance_class = 'storage_premium_perf29'
  and storage_target = 'block'
  and block_size = '4k'
  and io_engine in ('psync', 'io_uring')
")
metric_box(
  latency_engine_p50,
  x = "io_engine",
  y = "latency_us",
  fill = "io_engine",
  title = "P50 latency by I/O engine",
  ylab = "P50 latency (us)"
)
```

## Block Size Impact

The rest of the latency section focuses on `4k` because it is the latency-oriented workload. The following plots are included only to make the block-size effect visible; `128k` latency should not be mixed into the other latency comparisons. These block-size plots compare `io_uring/4k/iodepth=32` with `io_uring/128k/iodepth=16`.

### Block Storage

Filter used: `benchmark_machine_type = g2a.120d`, `block_volume_performance_class = storage_premium_perf29`, `storage_target = block`, `io_engine = io_uring`. Block size is the compared dimension and is therefore shown on the x-axis. Note that the `4k` measurements use `iodepth = 32`, while the `128k` measurements use `iodepth = 16`.

#### P99

```{r latency-block-size, fig.width=12, fig.height=7}
latency_block_size <- sql("
select block_size, benchmark_rw_mode,
       primary_clat_p99_ns / 1000.0 as latency_us
from fio
where valid_measurement
  and benchmark_machine_type = 'g2a.120d'
  and block_volume_performance_class = 'storage_premium_perf29'
  and storage_target = 'block'
  and io_engine = 'io_uring'
  and block_size in ('4k', '128k')
")
metric_box(
  latency_block_size,
  x = "block_size",
  y = "latency_us",
  fill = "block_size",
  title = "Block storage P99 latency by block size",
  ylab = "P99 latency (us)"
)
```

#### P50

```{r latency-block-size-p50, fig.width=12, fig.height=7}
latency_block_size_p50 <- sql("
select block_size, benchmark_rw_mode,
       primary_clat_p50_ns / 1000.0 as latency_us
from fio
where valid_measurement
  and benchmark_machine_type = 'g2a.120d'
  and block_volume_performance_class = 'storage_premium_perf29'
  and storage_target = 'block'
  and io_engine = 'io_uring'
  and block_size in ('4k', '128k')
")
metric_box(
  latency_block_size_p50,
  x = "block_size",
  y = "latency_us",
  fill = "block_size",
  title = "Block storage P50 latency by block size",
  ylab = "P50 latency (us)"
)
```

### Local Storage

Filter used: `benchmark_machine_type = g2a.120d`, `block_volume_performance_class = storage_premium_perf29`, `storage_target = local`, `io_engine = io_uring`. Block size is the compared dimension and is therefore shown on the x-axis. Note that the `4k` measurements use `iodepth = 32`, while the `128k` measurements use `iodepth = 16`.

#### P99

```{r latency-block-size-local, fig.width=12, fig.height=7}
latency_block_size_local <- sql("
select block_size, benchmark_rw_mode,
       primary_clat_p99_ns / 1000.0 as latency_us
from fio
where valid_measurement
  and benchmark_machine_type = 'g2a.120d'
  and block_volume_performance_class = 'storage_premium_perf29'
  and storage_target = 'local'
  and io_engine = 'io_uring'
  and block_size in ('4k', '128k')
")
metric_box(
  latency_block_size_local,
  x = "block_size",
  y = "latency_us",
  fill = "block_size",
  title = "Local storage P99 latency by block size",
  ylab = "P99 latency (us)"
)
```

#### P50

```{r latency-block-size-local-p50, fig.width=12, fig.height=7}
latency_block_size_local_p50 <- sql("
select block_size, benchmark_rw_mode,
       primary_clat_p50_ns / 1000.0 as latency_us
from fio
where valid_measurement
  and benchmark_machine_type = 'g2a.120d'
  and block_volume_performance_class = 'storage_premium_perf29'
  and storage_target = 'local'
  and io_engine = 'io_uring'
  and block_size in ('4k', '128k')
")
metric_box(
  latency_block_size_local_p50,
  x = "block_size",
  y = "latency_us",
  fill = "block_size",
  title = "Local storage P50 latency by block size",
  ylab = "P50 latency (us)"
)
```

## Storage Target Impact

Filter used: `benchmark_machine_type = g2a.120d`, `block_volume_performance_class = storage_premium_perf29`, `io_engine = io_uring`, `block_size = 4k`, `iodepth = 32`.

### P99

```{r latency-target, fig.width=12, fig.height=7}
latency_target <- sql("
select storage_target, benchmark_rw_mode,
       primary_clat_p99_ns / 1000.0 as latency_us
from fio
where valid_measurement
  and benchmark_machine_type = 'g2a.120d'
  and block_volume_performance_class = 'storage_premium_perf29'
  and storage_target in ('local', 'block')
  and io_engine = 'io_uring'
  and block_size = '4k'
")
metric_box(
  latency_target,
  x = "storage_target",
  y = "latency_us",
  fill = "storage_target",
  title = "P99 latency by storage target",
  ylab = "P99 latency (us)"
)
```

### P50

```{r latency-target-p50, fig.width=12, fig.height=7}
latency_target_p50 <- sql("
select storage_target, benchmark_rw_mode,
       primary_clat_p50_ns / 1000.0 as latency_us
from fio
where valid_measurement
  and benchmark_machine_type = 'g2a.120d'
  and block_volume_performance_class = 'storage_premium_perf29'
  and storage_target in ('local', 'block')
  and io_engine = 'io_uring'
  and block_size = '4k'
")
metric_box(
  latency_target_p50,
  x = "storage_target",
  y = "latency_us",
  fill = "storage_target",
  title = "P50 latency by storage target",
  ylab = "P50 latency (us)"
)
```

```{r latency-summary}
latency_summary <- sql("
select benchmark_machine_type, block_volume_performance_class, storage_target,
       benchmark_rw_mode, io_engine, block_size, iodepth,
       round(median(primary_clat_mean_ns) / 1000.0, 2) as median_avg_us,
       round(median(primary_clat_p50_ns) / 1000.0, 2) as median_p50_us,
       round(median(primary_clat_p99_ns) / 1000.0, 2) as median_p99_us,
       round(median(primary_clat_p999_ns) / 1000.0, 2) as median_p999_us,
       count(*) as repetitions
from fio
where valid_measurement
  and block_size = '4k'
group by 1, 2, 3, 4, 5, 6, 7
order by 1, 2, 3, 4, 5, 6, 7
")
kable(latency_summary, caption = "Latency summary for 4k measurements")
```

# OS Tuning Coverage

The current dataset does not contain paired `standard` and `tuned` storage runs, so there is no meaningful OS tuning impact plot yet.

```{r tuning-coverage}
tuning_coverage <- sql("
select os_tuning, count(*) as repetitions
from fio
where valid_measurement
group by 1
order by 1
")
kable(tuning_coverage, caption = "OS tuning coverage in valid fio repetitions")
```

# Diagnostics

```{r failures}
if (nrow(sql("select * from failures")) == 0) {
  cat("No failed fio runs were captured.")
} else {
  failure_table <- sql("
  select run_id, scenario_name, benchmark_name, storage_target, repetition, fio_error, failure_reason
  from failures
  order by run_id, scenario_name, benchmark_name, storage_target, repetition
  ")
  kable(failure_table, caption = "Failed fio repetitions")
}
```

```{r local-target-coverage}
local_summary <- sql("
select benchmark_machine_type, block_volume_performance_class, storage_target,
       benchmark_rw_mode, io_engine, block_size,
       sum(case when valid_measurement then 1 else 0 end) as valid_repetitions,
       sum(case when not valid_measurement then 1 else 0 end) as invalid_repetitions
from fio
where storage_target = 'local'
group by 1, 2, 3, 4, 5, 6
order by 1, 2, 3, 4, 5, 6
")
if (nrow(local_summary) == 0) {
  cat("No local-target measurements were parsed.")
} else {
  kable(local_summary, caption = "Local-target coverage")
}
```
